\startcomponent component_Links
\product product_TheRightToTheCity
\project project_MasterThesis

\starttext
\chapter[links]{Links}

\startREF%
%
Bellin, C., Gaswerk Grasbrook, Magdeburger Hafen, Geschichte Hamburger Hafen in Fotos. {\em Historische Hamburger Luftbilder}. Available at: \goto{\hyphenatedurl{http://www.hamburger-fotoarchiv.de/bilder_hafen/frames/frames_267_2417_luftaufnahme_hamburg.html}} [url(hafencityPortArea)] [Accessed January 9, 2011]. \nl%
%
BFSC, Barcelona Model of Urban Regeneration. {\em Barcelona Field Studies Centre}. Available at: \goto{\hyphenatedurl{http://geographyfieldwork.com/BarcelonaModel2.htm}} [url(barcelonaModel)] [Accessed January 10, 2011]. \nl%
%
CDRJ, 2010. Histórico do Porto. {\em Companhia Docas do Rio de Janeiro}. Available at: \goto{\hyphenatedurl{http://www.portosrio.gov.br/node/4}} [url(rioPortArea)] [Accessed January 13, 2011]. \nl%
%
cefetsp, CORTIÇOS. {\em CORTIÇOS}. Available at: \goto{\hyphenatedurl{http://www.cefetsp.br/edu/eso/geografia/corticos261.html}} [url(corticios)] [Accessed January 13, 2011]. \nl%
%
galataport.org, 2010. GALATAPORT: Galaport Projesi ile ilgili tum bilgiler burada. {\em Galataport Karaköy İstanbul Istanbul}. Available at: \goto{\hyphenatedurl{http://www.galataport.org/}} [url(galataPortProject)] [Accessed January 12, 2011]. \nl%
%
GaWC, 2010. GaWC - Globalization and World Cities. {\em Globalization and World Cities Research Network}. Available at: \goto{\hyphenatedurl{http://www.lboro.ac.uk/gawc/index.html}} [url(gawc)] [Accessed December 1, 2010]. \nl%
%
HafenCity Hamburg GmbH, 2010a. Am Sandtorkai / Dalmannkai - Projekt 24: Elbphilharmonie. {\em HafenCity Hamburg}. Available at: \goto{\hyphenatedurl{http://www.hafencity.com/de/am-sandtorkai-dalmannkai/projekt-24-elbphilharmonie.html}} [url(hafencityElbphilharmonie)] [Accessed January 9, 2011]. \nl%
%
HafenCity Hamburg GmbH, 2010b. Das Hamburg Cruise Center HafenCity. {\em HafenCity Hamburg}. Available at: \goto{\hyphenatedurl{http://www.hafencity.com/de/infocenter/das-hamburg-cruise-center-hafencity.html}} [url(hafencitySeaport)] [Accessed January 9, 2011]. \nl%
%
HafenCity Hamburg GmbH, 2010c. HafenCity Hamburg. {\em HafenCity Hamburg}. Available at: \goto{\hyphenatedurl{http://www.hafencity.com/index.php?set_language=de&cccpage=staedtebau_artikel&show=artikel&item=13}} [url(hafencity)] [Accessed January 9, 2011]. \nl%
%
Harvey, D., 2008. The Right to the City. {\em New Left Review}, (53). Available at: \goto{\hyphenatedurl{http://www.newleftreview.org/?page=article&view=2740}} [url(http://www.newleftreview.org/?page=article&view=2740)] [Accessed July 19, 2010]. \nl%
%
HGK, 2010a. Chronologie. {\em Modernes Köln}. Available at: \goto{\hyphenatedurl{http://www.moderneskoeln.de/WETTBEWERBE.htm}} [url(rheinauhafen1992)] [Accessed January 10, 2011]. \nl%
%
HGK, 2010b. Pandion Vista. {\em Modernes Köln}. Available at: \goto{\hyphenatedurl{http://www.moderneskoeln.de/Die PROJEKTE/3 KranhausVista.htm}} [url(kranhausPandion)] [Accessed January 10, 2011]. \nl%
%
HGK, 2010c. Rheinauhafen. {\em Modernes Köln}. Available at: \goto{\hyphenatedurl{http://www.moderneskoeln.de/Rheinauhafen.htm}} [url(rheinauhafen)] [Accessed January 10, 2011]. \nl%
%
HGK, 2010d. Siebengebirge. {\em Modernes Köln}. Available at: \goto{\hyphenatedurl{http://www.moderneskoeln.de/Die PROJEKTE/9 SIEBEN.htm}} [url(rheinauhafenSiebengebirge)] [Accessed January 10, 2011]. \nl%
%
HGK, 2010e. Wohnwer[f]t 18.20. {\em Modernes Köln}. Available at: \goto{\hyphenatedurl{http://www.moderneskoeln.de/Die PROJEKTE/13 WW.htm}} [url(rheinauhafenWohnwerft)] [Accessed January 10, 2011]. \nl%
%
Loughborough University, 2010. Loughborough University. {\em Loughborough University}. Available at: \goto{\hyphenatedurl{http://www.lboro.ac.uk/}} [url(loughborough)] [Accessed December 1, 2010]. \nl%
%
Pela Moradia, 2010. Pela Moradia. {\em Pela Moradia}. Available at: \goto{\hyphenatedurl{http://pelamoradia.wordpress.com/}} [url(rioSocialMovementMoradia)] [Accessed November 9, 2010]. \nl%
%
Rio Negócios, 2010a. 2014 World Cup. {\em Rio Negócios}. Available at: \goto{\hyphenatedurl{http://www.rio-negocios.com/site/en/2014-world-cup/}} [url(rio2014)] [Accessed January 13, 2011]. \nl%
%
Rio Negócios, 2010b. 2016 Olympics. {\em Rio Negócios}. Available at: \goto{\hyphenatedurl{http://www.rio-negocios.com/site/en/2016-olympics/}} [url(rio2016)] [Accessed January 13, 2011]. \nl%
%
Rio Prefeitura \& CDURP, 2010. Projeto Porto Maravilha. {\em Projeto Porto Maravilha}. Available at: \goto{\hyphenatedurl{http://www.portomaravilhario.com.br/cdurp/}} [url(rioProjetoPorto)] [Accessed January 13, 2011]. \nl%
%
RSK, 2010. Rheinauhafen. {\em Köln Marina RSK}. Available at: \goto{\hyphenatedurl{http://www.rheinau-sporthafen.de/}} [url(rheinauhafenSporthafen)] [Accessed January 10, 2011]. \nl%
%
RVG, 2010. Das Konzept des Rheinauhafens. {\em Rheinauhafen Köln}. Available at: \goto{\hyphenatedurl{http://www.rheinauhafen-koeln.de/Konzept}} [url(rheinauhafenIntegrate)] [Accessed January 10, 2011]. \nl%
%
da Silva, C., 2009. As ocupações de prédios vazios e o esvaziamento do centro da cidade do Rio de Janeiro. {\em ChiqdaSilva}. Available at: \goto{\hyphenatedurl{http://www.chiqdasilva.com/site/index.php?option=com_content&view=article&id=56:imgtxt01&catid=3:textos&Itemid=4}} [url(occupationsRio)] [Accessed November 5, 2010]. \nl%
%
STUDIOSarchitecture, 2010. Galata Port. {\em STUDIOSarchitecture}. Available at: \goto{\hyphenatedurl{http://www.studiosarchitecture.com/projects/65}} [url(galataPort)] [Accessed January 11, 2011]. \nl%
%
Wikipedia, 2010. Agribusiness. {\em Wikipedia, the free encyclopedia}. Available at: \goto{\hyphenatedurl{https://secure.wikimedia.org/wikipedia/en/wiki/Agribusiness}} [url(wikiEnAgribusiness)] [Accessed December 1, 2010]. \nl%
%
Wikipedia, 2011. Cologne. {\em Wikipedia, the free encyclopedia}. Available at: \goto{\hyphenatedurl{https://secure.wikimedia.org/wikipedia/en/wiki/Cologne}} [url(wikiEnColognes)] [Accessed January 10, 2011]. \nl%
%
Wikipedia, 2010a. Condominium. {\em Wikipedia, the free encyclopedia}. Available at: \goto{\hyphenatedurl{https://secure.wikimedia.org/wikipedia/en/wiki/Condos}} [url(wikiEnCondos)] [Accessed January 10, 2011]. \nl%
%
Wikipedia, 2010b. David Harvey (Geograph). {\em Wikipedia}. Available at: \goto{\hyphenatedurl{https://secure.wikimedia.org/wikipedia/de/wiki/David_Harvey_(Geograph)}} [url(wikiEnHarveys)] [Accessed November 23, 2010]. \nl%
%
Wikipedia, 2011. Favela. {\em Wikipedia, the free encyclopedia}. Available at: \goto{\hyphenatedurl{https://secure.wikimedia.org/wikipedia/en/wiki/Favela}} [url(wikiEnFavela)] [Accessed January 13, 2011]. \nl%
%
Wikipedia, 2001. HafenCity. {\em Wikipedia, the free encyclopedia}. Available at: \goto{\hyphenatedurl{https://secure.wikimedia.org/wikipedia/de/wiki/HafenCity}} [url(wikiEnHamburgs)] [Accessed January 9, 2011]. \nl%
%
Wikipedia, 2010. Henri Lefebvre. {\em Wikipedia, the free encyclopedia}. Available at: \goto{\hyphenatedurl{http://en.wikipedia.org/wiki/Henri_Lefebvre}} [url(wikiEnLefebfre)] [Accessed November 19, 2010]. \nl%
%
Wikipedia, 2011. Istanbul. {\em Wikipedia, the free encyclopedia}. Available at: \goto{\hyphenatedurl{https://secure.wikimedia.org/wikipedia/en/wiki/Istanbul}} [url(wikiEnIstanbul)] [Accessed January 11, 2011]. \nl%
%
Wikipedia, 2010a. John Friedmann. {\em Wikipedia, the free encyclopedia}. Available at: \goto{\hyphenatedurl{https://secure.wikimedia.org/wikipedia/en/wiki/John_Friedmann}} [url(wikiEnFriedmann)] [Accessed January 14, 2011]. \nl%
%
Wikipedia, 2010b. Karaköy. {\em Wikipedia, the free encyclopedia}. Available at: \goto{\hyphenatedurl{https://secure.wikimedia.org/wikipedia/en/wiki/Karaköy}} [url(wikiEnGalata)] [Accessed January 11, 2011]. \nl%
%
Wikipedia, 2010c. Kranhaus. {\em Wikipedia, the free encyclopedia}. Available at: \goto{\hyphenatedurl{https://secure.wikimedia.org/wikipedia/de/wiki/Kranhaus}} [url(wikiDeKranhaus)] [Accessed January 10, 2011]. \nl%
%
Wikipedia, 2010d. Manuel Castells. {\em Wikipedia, the free encyclopedia}. Available at: \goto{\hyphenatedurl{https://secure.wikimedia.org/wikipedia/en/wiki/Manuel_Castells}} [url(wikiEnCastells)] [Accessed December 1, 2010]. \nl%
%
Wikipedia, 2010e. Opera Australia. {\em Wikipedia, the free encyclopedia}. Available at: \goto{\hyphenatedurl{https://secure.wikimedia.org/wikipedia/en/wiki/Sydney_Opera}} [url(wikiEnSydneyOpera)] [Accessed January 9, 2011]. \nl%
%
Wikipedia, 2010f. Peter Hall (urbanist). {\em Wikipedia, the free encyclopedia}. Available at: \goto{\hyphenatedurl{https://secure.wikimedia.org/wikipedia/en/wiki/Peter_Hall_(urbanist)}} [url(wikiEnPeterHall)] [Accessed November 25, 2010]. \nl%
%
Wikipedia, 2011. Rio de Janeiro. {\em Wikipedia, the free encyclopedia}. Available at: \goto{\hyphenatedurl{https://secure.wikimedia.org/wikipedia/en/wiki/Rio_de_janeiro\#Port}} [url(wikiEnRio)] [Accessed January 13, 2011]. \nl%
%
Wikipedia, 2010a. Saskia Sassen. {\em Wikipedia, the free encyclopedia}. Available at: \goto{\hyphenatedurl{https://secure.wikimedia.org/wikipedia/en/wiki/Saskia_Sassen}} [url(wikiEnSassens)] [Accessed November 23, 2010]. \nl%
%
Wikipedia, 2010b. Severinsviertel. {\em Wikipedia, the free encyclopedia}. Available at: \goto{\hyphenatedurl{https://secure.wikimedia.org/wikipedia/de/wiki/Köln-Altstadt-\#Severinsviertel}} [url(wikiDeSeverinsviertel)] [Accessed January 10, 2011]. \nl%
%
Wikipédia, 2011. Porto de Itaguaí. {\em Wikipédia, a enciclopédia livre}. Available at: \goto{\hyphenatedurl{https://secure.wikimedia.org/wikipedia/pt/wiki/Porto_de_Sepetiba}} [url(rioPortoSepetiba)] [Accessed January 13, 2011]. \nl%
%
\stopREF%

\stoptext

\stopcomponent
