\environment envCmdRTC

\startenvironment envRupRefRttc

\define\myRefsOld%
{%
\startREF%
Bauriedl, S., 2007. Die Inszenierung des öffentlichen Raums für eine neue Urbanität: beispielsweise HafenCity. {\em THE THING Hamburg}. Available at: \goto{\hyphenatedurl{http://www.thing-hamburg.de/index.php?id=497}} [url(http://www.thing-hamburg.de/index.php?id=497)] [Accessed January 9, 2011].%
\nl%
Beaverstock, J.V., Faulconbridge, J.R. \& Hoyler, M., 2009. {\em Capitalism and the City}, Loughborough University: GaWC. Available at: \goto{\hyphenatedurl{http://www.lboro.ac.uk/gawc/rb/rb322.html}} [url(http://www.lboro.ac.uk/gawc/rb/rb322.html)] [Accessed November 28, 2010].%
\nl%
Bischoff, J., Joho, M. \& Scheller, A., 2009. Hamburg als Paradigma: Neoliberale Stadtpolitik konkret. {\em DbWi}. Available at: \goto{\hyphenatedurl{http://www.bdwi.de/forum/archiv/archiv/2380945.html}} [url(http://www.bdwi.de/forum/archiv/archiv/2380945.html)] [Accessed January 9, 2011].%
\nl%
Bischof, K., 2007. {\em Waterfront Revitalization in Riga: The case of Kipsala. Master Thesis. University of Turku}. Available at: \goto{\hyphenatedurl{http://balticstudies.utu.fi/master/thesisarchive/steffi_master_thesis_kipsala.pdf}} [url(http://balticstudies.utu.fi/master/thesisarchive/steffi_master_thesis_kipsala.pdf)].%
\nl%
Blenck, J., Nipper, J. \& Wiktorin, D., 2001. {\em Köln: der historisch-topographische Atlas}, Köln: Emons.%
\nl%
Brunet, F., 1995. {\em An economic analysis of the Barcelona’92 Olympic Games: resources, financing and impacts}. In The Keys of success: the social, sporting, economic and communications impact of Barcelona’92.  Barcelona: Servei de Publicacions de la Universitat Autònoma de Barcelona, pp. 203-237. Available at: \goto{\hyphenatedurl{http://olympicstudies.uab.es/pdf/wp030_eng.pdf}} [url(http://olympicstudies.uab.es/pdf/wp030_eng.pdf)].%
\nl%
Bruttomesso, R., 1993. {\em Working on the Water's Edge}. In Waterfronts: A new frontier for cities on water.  Venice:: International Centre Cities on Water. Available at: \goto{\hyphenatedurl{http://www.citiesonwater.com/sito/pubblicazioni/waterfronts/editoriale.htm}} [url(http://www.citiesonwater.com/sito/pubblicazioni/waterfronts/editoriale.htm)] [Accessed December 19, 2010].%
\nl%
Butuner, B., 2006. {\em Waterfront Revitalization as a Challenging Urban Issue}. In ISoCaRP Congress. Available at: \goto{\hyphenatedurl{http://www.isocarp.net/Data/case_studies/792.pdf}} [url(http://www.isocarp.net/Data/case_studies/792.pdf)].%
\nl%
Castells, M., 2004. {\em Space of Flows, Space of Places: Materials for a Theory of Urbanism in the Information Age}. In The Cybercities Reader.  London; New York: Routledge, pp. 82-93.%
\nl%
COHRE, 2007. Mega-Events, Forced Evictions and Displacements. Available at: \goto{\hyphenatedurl{http://www.cohre.org/sites/default/files/fact_sheet_mega-events_5_june_2007.pdf}} [url(http://www.cohre.org/sites/default/files/fact_sheet_mega-events_5_june_2007.pdf)] [Accessed December 5, 2010].%
\nl%
Davidson, M. \& Lees, L., 2005. New-build ‘gentrification’ and London’s riverside renaissance. {\em Environment and Planning A}, 37(7), 1165-1190. Available at: \goto{\hyphenatedurl{http://www.envplan.com/abstract.cgi?id=a3739}} [url(http://www.envplan.com/abstract.cgi?id=a3739)].%
\nl%
Dietmar, C. \& Rackosczy, C.P., 2002. {\em Köln, der Rhein, das Meer : 2000 Jahre Kölner Schifffahrts- und Hafengeschichte}, Köln: Emons.%
\nl%
Dumbe Essoka, J., 2003. {\em Brownfields Revitalization Projects: Displacement of the Dispossessed. Doctor of Philosophy. Drexel University}. Available at: \goto{\hyphenatedurl{http://citeseerx.ist.psu.edu/viewdoc/download?doi=10.1.1.122.275&rep=rep1&type=pdf}} [url(http://citeseerx.ist.psu.edu/viewdoc/download?doi=10.1.1.122.275&rep=rep1&type=pdf)].%
\nl%
E. Park, R., 1967. {\em On Social Control and Collective Behavior}. In The Heritage of Sociology.  Chicago, London: University of Chicago Press.%
\nl%
Fox, M., 2010. Brazil’s World Cup Development Debacle. {\em Upside Down World}. Available at: \goto{\hyphenatedurl{http://upsidedownworld.org/main/brazil-archives-63/2316-brazils-world-cup-development-debacle-?tmpl=component&print=1&page=}} [url(http://upsidedownworld.org/main/brazil-archives-63/2316-brazils-world-cup-development-debacle-?tmpl=component&print=1&page=)] [Accessed December 7, 2010].%
\nl%
Friedmann, J. \& Wolff, G., 1982. World city formation: an agenda for research and action. {\em International Journal of Urban and Regional Research}, 6(3), 309-344. Available at: \goto{\hyphenatedurl{http://doi.wiley.com/10.1111/j.1468-2427.1982.tb00384.x}} [url(http://doi.wiley.com/10.1111/j.1468-2427.1982.tb00384.x)].%
\nl%
Greene, S.J., 2003. Staged Cities: Mega-events, Slum Clearance, and Global Capital. {\em Yale Human Rights \& Development Law Journal}, 6, 161-187. Available at: \goto{\hyphenatedurl{http://www.law.yale.edu/documents/pdf/LawJournals/greene.pdf}} [url(http://www.law.yale.edu/documents/pdf/LawJournals/greene.pdf)] [Accessed December 4, 2010].%
\nl%
HafenCity Hamburg GmbH, 2006. Hafencity Hamburg: der Masterplan. Available at: \goto{\hyphenatedurl{}} [url()] [Accessed January 5, 2011].%
\nl%
HafenCity Hamburg GmbH, 2010. Projekte: Einblicke in die aktuellen Entwicklungen. Available at: \goto{\hyphenatedurl{}} [url()] [Accessed January 5, 2011].%
\nl%
Hall, P., 1966. {\em World Cities 1. ed.}, Weidenfeld \& N.%
\nl%
Harvey, D., 2008. The Right to the City. {\em New Left Review}, (53). Available at: \goto{\hyphenatedurl{http://www.newleftreview.org/?page=article&view=2740}} [url(http://www.newleftreview.org/?page=article&view=2740)] [Accessed July 19, 2010].%
\nl%
HGK, 2010a. Chronologie. {\em Modernes Köln}. Available at: \goto{\hyphenatedurl{http://www.moderneskoeln.de/WETTBEWERBE.htm}} [url(http://www.moderneskoeln.de/WETTBEWERBE.htm)] [Accessed January 10, 2011].%
\nl%
HGK, 2010b. Siebengebirge. {\em Modernes Köln}. Available at: \goto{\hyphenatedurl{http://www.moderneskoeln.de/Die PROJEKTE/9 SIEBEN.htm}}[url(http://www.moderneskoeln.de/Die PROJEKTE/9 SIEBEN.htm)] [Accessed January 10, 2011].%
\nl%
HGK, 2010c. Wohnwer[f]t 18.20. {\em Modernes Köln}. Available at: \goto{\hyphenatedurl{http://www.moderneskoeln.de/Die PROJEKTE/13 WW.htm}} [url(http://www.moderneskoeln.de/Die PROJEKTE/13 WW.htm)] [Accessed January 10, 2011].%
\nl%
Hogan, J.P., 2006. The Politics of Urban Regeneration. {\em Progress in Irish Urban Studies}, 2, 27-37. Available at: \goto{\hyphenatedurl{http://www.fius.ie/Documents/Jhogan_PIUS_Vol.2.pdf}} [url(http://www.fius.ie/Documents/Jhogan_PIUS_Vol.2.pdf)] [Accessed December 20, 2010].%
\nl%
Höhmann, I., 2010. Rheinauhafen Köln: Vorzeigequartier wartet auf Anschluss. {\em Wohnen - Immobilien - FAZ.NET}. Available at: \goto{\hyphenatedurl{http://www.faz.net/s/Rub8E0FC0CD826A4ACA80504FD9153A70F2/Doc\~E0CB48A76EDA6434784B7C3A44126DEEA\~ATpl\~Ecommon\~Scontent.html}} [url(http://www.faz.net/s/Rub8E0FC0CD826A4ACA80504FD9153A70F2/Doc\~E0CB48A76EDA6434784B7C3A44126DEEA\~ATpl\~Ecommon\~Scontent.html)] [Accessed January 11, 2011].%
\nl%
Holm, A., 2010. „Recht auf Stadt“ – Mehr als ein guter Slogan? {\em hEft, für literatur, stadt und alltag}, (21), 32-33. Available at: \goto{\hyphenatedurl{http://heft-online.de/index2.php?option=com_docman&task=doc_view&gid=28&Itemid=65}} [url(http://heft-online.de/index2.php?option=com_docman&task=doc_view&gid=28&Itemid=65)] [Accessed July 19, 2010].%
\nl%
immonet, 2010. Maritimes Wohnen im exklusiven Kranhaus im Rheinauhafen Köln, {\em immonet}. Available at: \goto{\hyphenatedurl{http://www.immonet.de/nordrhein-westfalen/koeln-innenstadt-altstadt-sued-etagenwohnung-mieten-10282d1217-1.html}} [url(http://www.immonet.de/nordrhein-westfalen/koeln-innenstadt-altstadt-sued-etagenwohnung-mieten-10282d1217-1.html)] [Accessed January 10, 2011].%
\nl%
IVV, 2008. Eine "weiße Wanne" gegen Hochwasser: die RVG sorgt für Lebens- und Wohnqualität am Rheinauhafen. {\em Wohnraum}, (11), 18-19. Available at: \goto{\hyphenatedurl{}} [url()] [Accessed December 20, 2010].%
\nl%
Kalkavan, Z., 2010. Port renovation projects fuel real estate boom in Galata. {\em Today's Zaman}. Available at: \goto{\hyphenatedurl{http://www.todayszaman.com/news-224611-port-renovation-projects-fuel-real-estate-boom-in-galata.html}} [url(http://www.todayszaman.com/news-224611-port-renovation-projects-fuel-real-estate-boom-in-galata.html)] [Accessed January 11, 2011].%
\nl%
Lefebvre, H., 1968. {\em Le Droit a la ville 1. ed.}, Paris: Anthropos.%
\nl%
Lefebvre, H., 1974. {\em Le droit à la ville suivi de Espace et politique 1. ed.}, Paris: Anthropos.%
\nl%
Lefebvre, H., 1991. {\em The production of space}, Oxford  OX  UK ;;Cambridge  Mass.  USA: Blackwell.%
\nl%
Lefebvre, H., 1996. {\em Writings on cities}, Cambridge  Mass  USA: Blackwell Publishers.%
\nl%
Les Cahiers, 2007. {\em Large Scale Urban Development Projects in Europe: Drivers of Change in City Regions}, INSTITUTE FOR URBAN PLANNING AND DEVELOPMENT OF THE ÎLE-DE-FRANCE REGION. Available at: \goto{\hyphenatedurl{http://www.iau-idf.fr/fileadmin/Etudes/etude_469/c146_gb.pdf}} [url(http://www.iau-idf.fr/fileadmin/Etudes/etude_469/c146_gb.pdf)].%
\nl%
Lopes de Souza, M., 2010. Welches Recht auf welche Stadt? Ein Plädoyer für politisch-strategische Klarheit. {\em Phase 2}. Available at: \goto{\hyphenatedurl{http://phase2.nadir.org/rechts.php?artikel=786&print=}} [url(http://phase2.nadir.org/rechts.php?artikel=786&print=)] [Accessed July 19, 2010].%
\nl%
Marshall, R., 2001. {\em Waterfronts in post industrial cities}, London ;;New York: Spon Press.%
\nl%
Niedt, C., 2006. Gentrification and the Grassroots: popular support in the revanchist suburb. {\em Journal of Urban Affairs}, 28(2), 99-120. Available at: \goto{\hyphenatedurl{http://www.hofstra.edu/pdf/Academics/css/css_jua_niedt.pdf}} [url(http://www.hofstra.edu/pdf/Academics/css/css_jua_niedt.pdf)] [Accessed December 20, 2010].%
\nl%
Pesch, M., 2002. eine Marina in Köln...... KAMC - BOOTE-Forum. {\em KAMC}. Available at: \goto{\hyphenatedurl{http://forum.boote-magazin.de/showthread.php?t=17392}} [url(http://forum.boote-magazin.de/showthread.php?t=17392)] [Accessed January 10, 2011].%
\nl%
Prigge, W., 2008. {\em Reading the Urban Revolution}. In Space, Difference, Everyday Life: Reading Henri Lefebvre.  New York, Abingdon: Routledge, pp. 46-61.%
\nl%
Purcell, M., 2002. Excavating Lefebvre: The right to the city and its urban politics of the inhabitant. {\em GeoJournal}, 58(2/3), 99-108. Available at: \goto{\hyphenatedurl{http://www.springerlink.com/content/m1856v64454767j9/}} [url(http://www.springerlink.com/content/m1856v64454767j9/)] [Accessed November 14, 2010].%
\nl%
RVG, 2010a. Büro \& Business im Rheinauhafen Köln. {\em Rheinauhafen Köln}. Available at: \goto{\hyphenatedurl{http://www.rheinauhafen-koeln.de/Business_Blaue_Seiten}} [url(http://www.rheinauhafen-koeln.de/Business_Blaue_Seiten)] [Accessed January 11, 2011].%
\nl%
RVG, 2010b. Das Konzept des Rheinauhafens. {\em Rheinauhafen Köln}. Available at: \goto{\hyphenatedurl{http://www.rheinauhafen-koeln.de/Konzept}} [url(http://www.rheinauhafen-koeln.de/Konzept)] [Accessed January 10, 2011].%
\nl%
Sassen, S., 1994. {\em Cities in a world economy}, Thousand Oaks  Calif.: Pine Forge Press.%
\nl%
Sassen, S., 1991. {\em The global city : New York, London, Tokyo 1. ed.}, Princeton  N.J.: Princeton University Press.%
\nl%
Shafik, R. \& Steele, J., 2010. {\em Tensions and Transformations in the Master Planning Process of Istanbul}. In Urban Transformation: Controversies, Contrasts, and Challenges. 14th IPHS CONFERENCE.  Iszanbul. Available at: \goto{\hyphenatedurl{}} [url()] [Accessed January 5, 2011].%
\nl%
Statistikamt Nord, 2007. Hamburger Stadtteil-Profile 2007 für die neuen Stadtteile: HafenCity, Hammerbrook, Sternschanze. Available at: \goto{\hyphenatedurl{}} [url()] [Accessed January 5, 2011].%
\nl%
Statistikamt Nord, 2008. Hamburger Stadtteil-Profile 2008 NORD.regional Band 5. Available at: \goto{\hyphenatedurl{}} [url()] [Accessed January 5, 2011].%
\nl%
Stredich, 2010. Tiefgarage Rheinauhafen, Köln. Available at: \goto{\hyphenatedurl{}} [url()] [Accessed January 5, 2011].%
\nl%
STUDIOSarchitecture, 2010. Galata Port. {\em STUDIOSarchitecture}. Available at: \goto{\hyphenatedurl{http://www.studiosarchitecture.com/projects/65}} [url(http://www.studiosarchitecture.com/projects/65)] [Accessed January 11, 2011].%
\nl%
Surborg, B., VanWynsberghe, R. \& Wyly, E., 2008. Mapping the Olympic growth machine. {\em City}, 12(3), 341-355. Available at: \goto{\hyphenatedurl{http://iocc.ca/documents/MappingTheOlympicGrowthMachine.pdf}} [url(http://iocc.ca/documents/MappingTheOlympicGrowthMachine.pdf)] [Accessed December 4, 2010]. \nl%
Tan, P., 2009. Istanbul: Widerstand im Stadtteil und gegenkultureller Raum. {\em Grundrisse}, (30). Available at: \goto{\hyphenatedurl{http://www.grundrisse.net/grundrisse30/Widerstand_im_Stadtteil.htm}} [url(http://www.grundrisse.net/grundrisse30/Widerstand_im_Stadtteil.htm)] [Accessed January 11, 2011].%
\nl%
Tan, P., 2007. Spatiality, Resistance and the Production of Locality.%
\nl%
Taylor, P.J., 2009. {\em Measuring the World City Network: New Results and Developments}, Loughborough: GaWC. Available at: \goto{\hyphenatedurl{http://www.lboro.ac.uk/gawc/rb/rb300.html}} [url(http://www.lboro.ac.uk/gawc/rb/rb300.html)] [Accessed December 3, 2010].%
\nl%
\stopREF%
}

\define\myLinksOld%
{%
\startREF%
Wikipedia, 2010a. David Harvey (Geograph). {\em Wikipedia}. Available at: \goto{\hyphenatedurl{https://secure.wikimedia.org/wikipedia/de/wiki/David_Harvey_(Geograph)}} [url(wikiEnHarveys)] [Accessed November 23, 2010].%
\nl%
Wikipedia, 2010b. Henri Lefebvre. {\em Wikipedia, the free encyclopedia}. Available at: \goto{\hyphenatedurl{http://en.wikipedia.org/wiki/Henri_Lefebvre}} [url(wikiEnLefebvre)] [Accessed November 19, 2010].%
\nl%
Wikipedia, 2010c. Saskia Sassen. {\em Wikipedia, the free encyclopedia}. Available at: \goto{\hyphenatedurl{https://secure.wikimedia.org/wikipedia/en/wiki/Saskia_Sassen}} [url(wikiEnSassen)] [Accessed November 23, 2010].%
\stopREF%
}

\define\myLinksOld%
{%
\startREF%
%
Bellin, C., Gaswerk Grasbrook, Magdeburger Hafen, Geschichte Hamburger Hafen in Fotos. {\em Historische Hamburger Luftbilder}. Available at:\goto{\hyphenatedurl{http://www.hamburger-fotoarchiv.de/bilder_hafen/frames/frames_267_2417_luftaufnahme_hamburg.html}} [url(hafencityPortArea)] [Accessed January 9, 2011]. \nl %
%
BFSC, Barcelona Model of Urban Regeneration. {\em Barcelona Field Studies Centre}. Available at: \goto{\hyphenatedurl{http://geographyfieldwork.com/BarcelonaModel2.htm}} [url(barcelonaModel)] [Accessed January 10, 2011]. \nl%
%
galataport.org, 2010. GALATAPORT: Galaport Projesi ile ilgili tum bilgiler burada. {\em Galataport Karaköy İstanbul Istanbul}. Available at: \goto{\hyphenatedurl{http://www.galataport.org/}} [url(galataPortProject)] [Accessed January 12, 2011]. \nl%
%
GaWC, 2010. GaWC - Globalization and World Cities. {\em Globalization and World Cities Research Network}. Available at: \goto{\hyphenatedurl{http://www.lboro.ac.uk/gawc/index.html}} [url(gawc)] [Accessed December 1, 2010]. \nl%
%
HafenCity Hamburg GmbH, 2010a. Am Sandtorkai / Dalmannkai - Projekt 24: Elbphilharmonie. {\em HafenCity Hamburg}. Available at: \goto{\hyphenatedurl{http://www.hafencity.com/de/am-sandtorkai-dalmannkai/projekt-24-elbphilharmonie.html}} [url(hafencityElbphilharmonie)] [Accessed January 9, 2011]. \nl%
%
HafenCity Hamburg GmbH, 2010b. Das Hamburg Cruise Center HafenCity. {\em HafenCity Hamburg}. Available at: \goto{\hyphenatedurl{http://www.hafencity.com/de/infocenter/das-hamburg-cruise-center-hafencity.html}} [url(hafencitySeaport)] [Accessed January 9, 2011]. \nl%
%
HafenCity Hamburg GmbH, 2010c. HafenCity Hamburg. {\em HafenCity Hamburg}. Available at: \goto{\hyphenatedurl{http://www.hafencity.com/index.php?set_language=de&cccpage=staedtebau_artikel&show=artikel&item=13}} [url(hafencity)] [Accessed January 9, 2011]. \nl%
%
Harvey, D., 2008. The Right to the City. {\em New Left Review}, (53). Available at: \goto{\hyphenatedurl{http://www.newleftreview.org/?page=article&view=2740}} [url(newLeftReviewRttc)] [Accessed July 19, 2010]. \nl%
%
HGK, 2010a. Pandion Vista. {\em Modernes Köln}. Available at: \goto{\hyphenatedurl{http://www.moderneskoeln.de/Die PROJEKTE/3 KranhausVista.htm}} [url(kranhausPandion)] [Accessed January 10, 2011]. \nl%
%
HGK, 2010b. Rheinauhafen. {\em Modernes Köln}. Available at: \goto{\hyphenatedurl{http://www.moderneskoeln.de/Rheinauhafen.htm}} [url(v)] [Accessed January 10, 2011]. \nl%
%
HGK, 2010c. Siebengebirge. {\em Modernes Köln}. Available at: \goto{\hyphenatedurl{http://www.moderneskoeln.de/Die PROJEKTE/9 SIEBEN.htm}} [url(rheinauhafenSiebengebirge)] [Accessed January 10, 2011]. \nl%
%
HGK, 2010d. Wohnwer[f]t 18.20. {\em Modernes Köln}. Available at: \goto{\hyphenatedurl{http://www.moderneskoeln.de/Die PROJEKTE/13 WW.htm}} [url(rheinauhafenWohnwerft)] [Accessed January 10, 2011]. \nl%
%
Loughborough University, 2010. Loughborough University. {\em Loughborough University}. Available at: \goto{\hyphenatedurl{http://www.lboro.ac.uk/}} [url(loughborough)] [Accessed December 1, 2010]. \nl%
%
RSK, 2010. Rheinauhafen. {\em Köln Marina RSK}. Available at: \goto{\hyphenatedurl{http://www.rheinau-sporthafen.de/}} [url(rheinauhafenSporthafen)] [Accessed January 10, 2011]. \nl%
%
RVG, 2010. Das Konzept des Rheinauhafens. {\em Rheinauhafen Köln}. Available at: \goto{\hyphenatedurl{http://www.rheinauhafen-koeln.de/Konzept}} [url(rheinauhafenIntegrate)] [Accessed January 10, 2011]. \nl%
%
Wikipedia, 2010. Agribusiness. {\em Wikipedia, the free encyclopedia}. Available at: \goto{\hyphenatedurl{https://secure.wikimedia.org/wikipedia/en/wiki/Agribusiness}} [url(wikiEnAgribusiness)] [Accessed December 1, 2010]. \nl%
%
Wikipedia, 2011. Cologne. {\em Wikipedia, the free encyclopedia}. Available at: \goto{\hyphenatedurl{https://secure.wikimedia.org/wikipedia/en/wiki/Cologne}} [url(wikiEnColognes)] [Accessed January 10, 2011]. \nl%
%
Wikipedia, 2010a. Condominium. {\em Wikipedia, the free encyclopedia}. Available at: \goto{\hyphenatedurl{https://secure.wikimedia.org/wikipedia/en/wiki/Condos}} [url(wikiEnCondos)] [Accessed January 10, 2011]. \nl%
%
Wikipedia, 2010b. David Harvey (Geograph). {\em Wikipedia}. Available at: \goto{\hyphenatedurl{https://secure.wikimedia.org/wikipedia/de/wiki/David_Harvey_(Geograph)}} [url(wikiEnHarveys)] [Accessed November 23, 2010]. \nl%
%
Wikipedia, 2001. HafenCity. {\em Wikipedia, the free encyclopedia}. Available at: \goto{\hyphenatedurl{https://secure.wikimedia.org/wikipedia/de/wiki/HafenCity}} [url(wikiEnHamburgs)] [Accessed January 9, 2011]. \nl%
%
Wikipedia, 2010. Henri Lefebvre. {\em Wikipedia, the free encyclopedia}. Available at: \goto{\hyphenatedurl{http://en.wikipedia.org/wiki/Henri_Lefebvre}} [url(wikiEnLefebfre)] [Accessed November 19, 2010]. \nl%
%
Wikipedia, 2011. Istanbul. {\em Wikipedia, the free encyclopedia}. Available at: \goto{\hyphenatedurl{https://secure.wikimedia.org/wikipedia/en/wiki/Istanbul}} [url(wikiEnIstanbul)] [Accessed January 11, 2011]. \nl%
%
Wikipedia, 2010a. Karaköy. {\em Wikipedia, the free encyclopedia}. Available at: \goto{\hyphenatedurl{https://secure.wikimedia.org/wikipedia/en/wiki/Karaköy}} [url(wikiEnGalata)] [Accessed January 11, 2011]. \nl%
%
Wikipedia, 2010b. Kranhaus. {\em Wikipedia, the free encyclopedia}. Available at: \goto{\hyphenatedurl{https://secure.wikimedia.org/wikipedia/de/wiki/Kranhaus}} [url(wikiDeKranhaus)] [Accessed January 10, 2011]. \nl%
%
Wikipedia, 2010c. Manuel Castells. {\em Wikipedia, the free encyclopedia}. Available at: \goto{\hyphenatedurl{https://secure.wikimedia.org/wikipedia/en/wiki/Manuel_Castells}} [url(wikiEnCastells)] [Accessed December 1, 2010]. \nl%
%
Wikipedia, 2010d. Opera Australia. {\em Wikipedia, the free encyclopedia}. Available at: \goto{\hyphenatedurl{https://secure.wikimedia.org/wikipedia/en/wiki/Sydney_Opera}} [url(wikiEnSydneyOpera)] [Accessed January 9, 2011]. \nl%
%
Wikipedia, 2010e. Peter Hall (urbanist). {\em Wikipedia, the free encyclopedia}. Available at: \goto{\hyphenatedurl{https://secure.wikimedia.org/wikipedia/en/wiki/Peter_Hall_(urbanist)}} [url(wikiEnPeterHall)] [Accessed November 25, 2010]. \nl%
%
Wikipedia, 2010f. Saskia Sassen. {\em Wikipedia, the free encyclopedia}. Available at: \goto{\hyphenatedurl{https://secure.wikimedia.org/wikipedia/en/wiki/Saskia_Sassen}} [url(wikiEnSassens)] [Accessed November 23, 2010]. \nl%
%
Wikipedia, 2010g. Severinsviertel. {\em Wikipedia, the free encyclopedia}. Available at: \goto{\hyphenatedurl{https://secure.wikimedia.org/wikipedia/de/wiki/Köln-Altstadt-Süd\#Severinsviertel}} [url(wikiDeSeverinsviertel)] [Accessed January 10, 2011]. \nl%
\stopREF%
}

\define\myLinks%
{%
\startREF%
Bellin, C., Gaswerk Grasbrook, Magdeburger Hafen, Geschichte Hamburger Hafen in Fotos. {\em Historische Hamburger Luftbilder}. Available at: \goto{\hyphenatedurl{http://www.hamburger-fotoarchiv.de/bilder_hafen/frames/frames_267_2417_luftaufnahme_hamburg.html}} [url(hafencityPortArea)] [Accessed January 9, 2011]. \nl%
%
BFSC, Barcelona Model of Urban Regeneration. {\em Barcelona Field Studies Centre}. Available at: \goto{\hyphenatedurl{http://geographyfieldwork.com/BarcelonaModel2.htm}} [url(barcelonaModel)] [Accessed January 10, 2011]. \nl%
%
CDRJ, 2010. Histórico do Porto. {\em Companhia Docas do Rio de Janeiro}. Available at: \goto{\hyphenatedurl{http://www.portosrio.gov.br/node/4}} [url(rioPortArea)] [Accessed January 13, 2011]. \nl%
%
cefetsp, CORTIÇOS. {\em CORTIÇOS}. Available at: \goto{\hyphenatedurl{http://www.cefetsp.br/edu/eso/geografia/corticos261.html}} [url(corticios)] [Accessed January 13, 2011]. \nl%
%
galataport.org, 2010. GALATAPORT: Galaport Projesi ile ilgili tum bilgiler burada. {\em Galataport Karaköy İstanbul Istanbul}. Available at: \goto{\hyphenatedurl{http://www.galataport.org/}} [url(galataPortProject)] [Accessed January 12, 2011]. \nl%
%
GaWC, 2010. GaWC - Globalization and World Cities. {\em Globalization and World Cities Research Network}. Available at: \goto{\hyphenatedurl{http://www.lboro.ac.uk/gawc/index.html}} [url(gawc)] [Accessed December 1, 2010]. \nl%
%
HafenCity Hamburg GmbH, 2010a. Am Sandtorkai / Dalmannkai - Projekt 24: Elbphilharmonie. {\em HafenCity Hamburg}. Available at: \goto{\hyphenatedurl{http://www.hafencity.com/de/am-sandtorkai-dalmannkai/projekt-24-elbphilharmonie.html}} [url(hafencityElbphilharmonie)] [Accessed January 9, 2011]. \nl%
%
HafenCity Hamburg GmbH, 2010b. Das Hamburg Cruise Center HafenCity. {\em HafenCity Hamburg}. Available at: \goto{\hyphenatedurl{http://www.hafencity.com/de/infocenter/das-hamburg-cruise-center-hafencity.html}} [url(hafencitySeaport)] [Accessed January 9, 2011]. \nl%
%
HafenCity Hamburg GmbH, 2010c. HafenCity Hamburg. {\em HafenCity Hamburg}. Available at: \goto{\hyphenatedurl{http://www.hafencity.com/index.php?set_language=de&cccpage=staedtebau_artikel&show=artikel&item=13}} [url(hafencity)] [Accessed January 9, 2011]. \nl%
%
Harvey, D., 2008. The Right to the City. {\em New Left Review}, (53). Available at: \goto{\hyphenatedurl{http://www.newleftreview.org/?page=article&view=2740}} [url(http://www.newleftreview.org/?page=article&view=2740)] [Accessed July 19, 2010]. \nl%
%
HGK, 2010a. Chronologie. {\em Modernes Köln}. Available at: \goto{\hyphenatedurl{http://www.moderneskoeln.de/WETTBEWERBE.htm}} [url(rheinauhafen1992)] [Accessed January 10, 2011]. \nl%
%
HGK, 2010b. Pandion Vista. {\em Modernes Köln}. Available at: \goto{\hyphenatedurl{http://www.moderneskoeln.de/Die PROJEKTE/3 KranhausVista.htm}} [url(kranhausPandion)] [Accessed January 10, 2011]. \nl%
%
HGK, 2010c. Rheinauhafen. {\em Modernes Köln}. Available at: \goto{\hyphenatedurl{http://www.moderneskoeln.de/Rheinauhafen.htm}} [url(rheinauhafen)] [Accessed January 10, 2011]. \nl%
%
HGK, 2010d. Siebengebirge. {\em Modernes Köln}. Available at: \goto{\hyphenatedurl{http://www.moderneskoeln.de/Die PROJEKTE/9 SIEBEN.htm}} [url(rheinauhafenSiebengebirge)] [Accessed January 10, 2011]. \nl%
%
HGK, 2010e. Wohnwer[f]t 18.20. {\em Modernes Köln}. Available at: \goto{\hyphenatedurl{http://www.moderneskoeln.de/Die PROJEKTE/13 WW.htm}} [url(rheinauhafenWohnwerft)] [Accessed January 10, 2011]. \nl%
%
Loughborough University, 2010. Loughborough University. {\em Loughborough University}. Available at: \goto{\hyphenatedurl{http://www.lboro.ac.uk/}} [url(loughborough)] [Accessed December 1, 2010]. \nl%
%
Pela Moradia, 2010. Pela Moradia. {\em Pela Moradia}. Available at: \goto{\hyphenatedurl{http://pelamoradia.wordpress.com/}} [url(rioSocialMovementMoradia)] [Accessed November 9, 2010]. \nl%
%
Rio Negócios, 2010a. 2014 World Cup. {\em Rio Negócios}. Available at: \goto{\hyphenatedurl{http://www.rio-negocios.com/site/en/2014-world-cup/}} [url(rio2014)] [Accessed January 13, 2011]. \nl%
%
Rio Negócios, 2010b. 2016 Olympics. {\em Rio Negócios}. Available at: \goto{\hyphenatedurl{http://www.rio-negocios.com/site/en/2016-olympics/}} [url(rio2016)] [Accessed January 13, 2011]. \nl%
%
Rio Prefeitura \& CDURP, 2010. Projeto Porto Maravilha. {\em Projeto Porto Maravilha}. Available at: \goto{\hyphenatedurl{http://www.portomaravilhario.com.br/cdurp/}} [url(rioProjetoPorto)] [Accessed January 13, 2011]. \nl%
%
RSK, 2010. Rheinauhafen. {\em Köln Marina RSK}. Available at: \goto{\hyphenatedurl{http://www.rheinau-sporthafen.de/}} [url(rheinauhafenSporthafen)] [Accessed January 10, 2011]. \nl%
%
RVG, 2010. Das Konzept des Rheinauhafens. {\em Rheinauhafen Köln}. Available at: \goto{\hyphenatedurl{http://www.rheinauhafen-koeln.de/Konzept}} [url(rheinauhafenIntegrate)] [Accessed January 10, 2011]. \nl%
%
da Silva, C., 2009. As ocupações de prédios vazios e o esvaziamento do centro da cidade do Rio de Janeiro. {\em ChiqdaSilva}. Available at: \goto{\hyphenatedurl{http://www.chiqdasilva.com/site/index.php?option=com_content&view=article&id=56:imgtxt01&catid=3:textos&Itemid=4}} [url(occupationsRio)] [Accessed November 5, 2010]. \nl%
%
STUDIOSarchitecture, 2010. Galata Port. {\em STUDIOSarchitecture}. Available at: \goto{\hyphenatedurl{http://www.studiosarchitecture.com/projects/65}} [url(galataPort)] [Accessed January 11, 2011]. \nl%
%
Wikipedia, 2010. Agribusiness. {\em Wikipedia, the free encyclopedia}. Available at: \goto{\hyphenatedurl{https://secure.wikimedia.org/wikipedia/en/wiki/Agribusiness}} [url(wikiEnAgribusiness)] [Accessed December 1, 2010]. \nl%
%
Wikipedia, 2011. Cologne. {\em Wikipedia, the free encyclopedia}. Available at: \goto{\hyphenatedurl{https://secure.wikimedia.org/wikipedia/en/wiki/Cologne}} [url(wikiEnColognes)] [Accessed January 10, 2011]. \nl%
%
Wikipedia, 2010a. Condominium. {\em Wikipedia, the free encyclopedia}. Available at: \goto{\hyphenatedurl{https://secure.wikimedia.org/wikipedia/en/wiki/Condos}} [url(wikiEnCondos)] [Accessed January 10, 2011]. \nl%
%
Wikipedia, 2010b. David Harvey (Geograph). {\em Wikipedia}. Available at: \goto{\hyphenatedurl{https://secure.wikimedia.org/wikipedia/de/wiki/David_Harvey_(Geograph)}} [url(wikiEnHarveys)] [Accessed November 23, 2010]. \nl%
%
Wikipedia, 2011. Favela. {\em Wikipedia, the free encyclopedia}. Available at: \goto{\hyphenatedurl{https://secure.wikimedia.org/wikipedia/en/wiki/Favela}} [url(wikiEnFavela)] [Accessed January 13, 2011]. \nl%
%
Wikipedia, 2001. HafenCity. {\em Wikipedia, the free encyclopedia}. Available at: \goto{\hyphenatedurl{https://secure.wikimedia.org/wikipedia/de/wiki/HafenCity}} [url(wikiEnHamburgs)] [Accessed January 9, 2011]. \nl%
%
Wikipedia, 2010. Henri Lefebvre. {\em Wikipedia, the free encyclopedia}. Available at: \goto{\hyphenatedurl{http://en.wikipedia.org/wiki/Henri_Lefebvre}} [url(wikiEnLefebfre)] [Accessed November 19, 2010]. \nl%
%
Wikipedia, 2011. Istanbul. {\em Wikipedia, the free encyclopedia}. Available at: \goto{\hyphenatedurl{https://secure.wikimedia.org/wikipedia/en/wiki/Istanbul}} [url(wikiEnIstanbul)] [Accessed January 11, 2011]. \nl%
%
Wikipedia, 2010a. John Friedmann. {\em Wikipedia, the free encyclopedia}. Available at: \goto{\hyphenatedurl{https://secure.wikimedia.org/wikipedia/en/wiki/John_Friedmann}} [url(wikiEnFriedmann)] [Accessed January 14, 2011]. \nl%
%
Wikipedia, 2010b. Karaköy. {\em Wikipedia, the free encyclopedia}. Available at: \goto{\hyphenatedurl{https://secure.wikimedia.org/wikipedia/en/wiki/Karaköy}} [url(wikiEnGalata)] [Accessed January 11, 2011]. \nl%
%
Wikipedia, 2010c. Kranhaus. {\em Wikipedia, the free encyclopedia}. Available at: \goto{\hyphenatedurl{https://secure.wikimedia.org/wikipedia/de/wiki/Kranhaus}} [url(wikiDeKranhaus)] [Accessed January 10, 2011]. \nl%
%
Wikipedia, 2010d. Manuel Castells. {\em Wikipedia, the free encyclopedia}. Available at: \goto{\hyphenatedurl{https://secure.wikimedia.org/wikipedia/en/wiki/Manuel_Castells}} [url(wikiEnCastells)] [Accessed December 1, 2010]. \nl%
%
Wikipedia, 2010e. Opera Australia. {\em Wikipedia, the free encyclopedia}. Available at: \goto{\hyphenatedurl{https://secure.wikimedia.org/wikipedia/en/wiki/Sydney_Opera}} [url(wikiEnSydneyOpera)] [Accessed January 9, 2011]. \nl%
%
Wikipedia, 2010f. Peter Hall (urbanist). {\em Wikipedia, the free encyclopedia}. Available at: \goto{\hyphenatedurl{https://secure.wikimedia.org/wikipedia/en/wiki/Peter_Hall_(urbanist)}} [url(wikiEnPeterHall)] [Accessed November 25, 2010]. \nl%
%
Wikipedia, 2011. Rio de Janeiro. {\em Wikipedia, the free encyclopedia}. Available at: \goto{\hyphenatedurl{https://secure.wikimedia.org/wikipedia/en/wiki/Rio_de_janeiro\#Port}} [url(wikiEnRio)] [Accessed January 13, 2011]. \nl%
%
Wikipedia, 2010a. Saskia Sassen. {\em Wikipedia, the free encyclopedia}. Available at: \goto{\hyphenatedurl{https://secure.wikimedia.org/wikipedia/en/wiki/Saskia_Sassen}} [url(wikiEnSassens)] [Accessed November 23, 2010]. \nl%
%
Wikipedia, 2010b. Severinsviertel. {\em Wikipedia, the free encyclopedia}. Available at: \goto{\hyphenatedurl{https://secure.wikimedia.org/wikipedia/de/wiki/Köln-Altstadt-\#Severinsviertel}} [url(wikiDeSeverinsviertel)] [Accessed January 10, 2011]. \nl%
%
Wikipédia, 2011. Porto de Itaguaí. {\em Wikipédia, a enciclopédia livre}. Available at: \goto{\hyphenatedurl{https://secure.wikimedia.org/wikipedia/pt/wiki/Porto_de_Sepetiba}} [url(rioPortoSepetiba)] [Accessed January 13, 2011]. \nl%
%
\stopREF%
}

\define\myRefs%
{%
\startREF%
Azevedo, A., 1890. {\em O Cortiço 1. ed.}, \nl%
%
Barcelona City Council, 2009. {\em Barcelona Bulletin}, Barcelona: Barcelona City Council. Available at: \goto{\hyphenatedurl{http://w3.bcn.cat/fitxers/premsa/bul262.679.pdf}} [url(http://w3.bcn.cat/fitxers/premsa/bul262.679.pdf)] [Accessed December 5, 2010]. \nl%
%
Bauriedl, S., 2007. Die Inszenierung des öffentlichen Raums für eine neue Urbanität: beispielsweise HafenCity. {\em THE THING Hamburg}. Available at: \goto{\hyphenatedurl{http://www.thing-hamburg.de/index.php?id=497}} [url(http://www.thing-hamburg.de/index.php?id=497)] [Accessed January 9, 2011]. \nl%
%
Beaverstock, J.V., Faulconbridge, J.R. \& Hoyler, M., 2009. {\em Capitalism and the City}, Loughborough University: GaWC. Available at: \goto{\hyphenatedurl{http://www.lboro.ac.uk/gawc/rb/rb322.html}} [url(http://www.lboro.ac.uk/gawc/rb/rb322.html)] [Accessed November 28, 2010]. \nl%
%
Bischoff, J., Joho, M. \& Scheller, A., 2009. Hamburg als Paradigma: Neoliberale Stadtpolitik konkret. {\em DbWi}. Available at: \goto{\hyphenatedurl{http://www.bdwi.de/forum/archiv/archiv/2380945.html}} [url(http://www.bdwi.de/forum/archiv/archiv/2380945.html)] [Accessed January 9, 2011]. \nl%
%
Bischof, K., 2007. {\em Waterfront Revitalization in Riga: The case of Kipsala. Master Thesis. University of Turku}. Available at: \goto{\hyphenatedurl{http://balticstudies.utu.fi/master/thesisarchive/steffi_master_thesis_kipsala.pdf}} [url(http://balticstudies.utu.fi/master/thesisarchive/steffi_master_thesis_kipsala.pdf)]. \nl%
%
Blenck, J., Nipper, J. \& Wiktorin, D., 2001. {\em Köln: der historisch-topographische Atlas}, Köln: Emons. \nl%
%
Brown, A. \& Kristiansen, A., 2009. Urban Policies and the Right to the City: Rights, responsibilities and citizenship. Available at: \goto{\hyphenatedurl{http://unesdoc.unesco.org/images/0017/001780/178090e.pdf}} [url(http://unesdoc.unesco.org/images/0017/001780/178090e.pdf)] [Accessed January 12, 2010]. \nl%
%
Brunet, F., 1995. {\em An economic analysis of the Barcelona’92 Olympic Games: resources, financing and impacts}. In The Keys of success: the social, sporting, economic and communications impact of Barcelona’92.  Barcelona: Servei de Publicacions de la Universitat Autònoma de Barcelona, pp. 203-237. Available at: \goto{\hyphenatedurl{http://olympicstudies.uab.es/pdf/wp030_eng.pdf}} [url(http://olympicstudies.uab.es/pdf/wp030_eng.pdf)]. \nl%
%
Bruttomesso, R., 1993. {\em Working on the Water's Edge}. In Waterfronts: A new frontier for cities on water.  Venice:: International Centre Cities on Water. Available at: \goto{\hyphenatedurl{http://www.citiesonwater.com/sito/pubblicazioni/waterfronts/editoriale.htm}} [url(http://www.citiesonwater.com/sito/pubblicazioni/waterfronts/editoriale.htm)] [Accessed December 19, 2010]. \nl%
%
Butuner, B., 2006. {\em Waterfront Revitalization as a Challenging Urban Issue}. In ISoCaRP Congress. Available at: \goto{\hyphenatedurl{http://www.isocarp.net/Data/case_studies/792.pdf}} [url(http://www.isocarp.net/Data/case_studies/792.pdf)]. \nl%
%
Castells, M., 2004. {\em Space of Flows, Space of Places: Materials for a Theory of Urbanism in the Information Age}. In The Cybercities Reader.  London; New York: Routledge, pp. 82-93. \nl%
%
COHRE, 2007. Mega-Events, Forced Evictions and Displacements. Available at: \goto{\hyphenatedurl{http://www.cohre.org/sites/default/files/fact_sheet_mega-events_5_june_2007.pdf}} [url(http://www.cohre.org/sites/default/files/fact_sheet_mega-events_5_june_2007.pdf)] [Accessed December 5, 2010]. \nl%
%
Davidson, M. \& Lees, L., 2005. New-build ‘gentrification’ and London’s riverside renaissance. {\em Environment and Planning A}, 37(7), 1165-1190. Available at: \goto{\hyphenatedurl{http://www.envplan.com/abstract.cgi?id=a3739}} [url(http://www.envplan.com/abstract.cgi?id=a3739)]. \nl%
%
Dietmar, C. \& Rackosczy, C.P., 2002. {\em Köln, der Rhein, das Meer : 2000 Jahre Kölner Schifffahrts- und Hafengeschichte}, Köln: Emons. \nl%
%
Dumbe Essoka, J., 2003. {\em Brownfields Revitalization Projects: Displacement of the Dispossessed. Doctor of Philosophy. Drexel University}. Available at: \goto{\hyphenatedurl{http://citeseerx.ist.psu.edu/viewdoc/download?doi=10.1.1.122.275&rep=rep1&type=pdf}} [url(http://citeseerx.ist.psu.edu/viewdoc/download?doi=10.1.1.122.275&rep=rep1&type=pdf)]. \nl%
%
E. Park, R., 1967. {\em On Social Control and Collective Behavior}. In The Heritage of Sociology.  Chicago, London: University of Chicago Press. \nl%
%
Ferreira Santos, J.C., 2005. Políticas Espaciais de Requalidicção Urbana na Área Central do Rio de Janeiro: nova estética da desintegração local e espetáculo da projeção global. {\em Revista Electrónica de Geografía y Ciencas Sociales}, 9(194 (43)). Available at: \goto{\hyphenatedurl{http://www.ub.edu/geocrit/sn/sn-194-43.htm}} [url(http://www.ub.edu/geocrit/sn/sn-194-43.htm)] [Accessed January 12, 2011]. \nl%
%
Fox, M., 2010. Brazil’s World Cup Development Debacle. {\em Upside Down World}. Available at: \goto{\hyphenatedurl{http://upsidedownworld.org/main/brazil-archives-63/2316-brazils-world-cup-development-debacle-?tmpl=component&print=1&page=}} [url(http://upsidedownworld.org/main/brazil-archives-63/2316-brazils-world-cup-development-debacle-?tmpl=component&print=1&page=)] [Accessed December 7, 2010]. \nl%
%
Friedmann, J. \& Wolff, G., 1982. World city formation: an agenda for research and action. {\em International Journal of Urban and Regional Research}, 6(3), 309-344. Available at: \goto{\hyphenatedurl{http://doi.wiley.com/10.1111/j.1468-2427.1982.tb00384.x}} [url(http://doi.wiley.com/10.1111/j.1468-2427.1982.tb00384.x)]. \nl%
%
Gilbert, L. \& Dikeç, M., 2008. {\em Right to the city: Policits of citizenship}. In Space, Difference, Everyday Life: Reading Henri Lefebvre.  New York: Routledge, pp. 250-261. \nl%
%
Greene, S.J., 2003. Staged Cities: Mega-events, Slum Clearance, and Global Capital. {\em Yale Human Rights \& Development Law Journal}, 6, 161-187. Available at: \goto{\hyphenatedurl{http://www.law.yale.edu/documents/pdf/LawJournals/greene.pdf}} [url(http://www.law.yale.edu/documents/pdf/LawJournals/greene.pdf)] [Accessed December 4, 2010]. \nl%
%
Guerreiro Urbano, 2010. Solidarity with the Guerreiro Urbano (Urban Warrior) Occupation. \nl%
%
HafenCity Hamburg GmbH, 2006. Hafencity Hamburg: der Masterplan. Available at: \goto{\hyphenatedurl{}} [url()] [Accessed January 5, 2011]. \nl%
%
HafenCity Hamburg GmbH, 2010. Projekte: Einblicke in die aktuellen Entwicklungen. Available at: \goto{\hyphenatedurl{}} [url()] [Accessed January 5, 2011]. \nl%
%
Hall, P., 1966. {\em World Cities 1. ed.}, Weidenfeld \& N. \nl%
%
Harvey, D., 2008. The Right to the City. {\em New Left Review}, (53). Available at: \goto{\hyphenatedurl{http://www.newleftreview.org/?page=article&view=2740}} [url(http://www.newleftreview.org/?page=article&view=2740)] [Accessed July 19, 2010]. \nl%
%
HGK, 2010a. Chronologie. {\em Modernes Köln}. Available at: \goto{\hyphenatedurl{http://www.moderneskoeln.de/WETTBEWERBE.htm}} [url(http://www.moderneskoeln.de/WETTBEWERBE.htm)] [Accessed January 10, 2011]. \nl%
%
HGK, 2010b. Siebengebirge. {\em Modernes Köln}. Available at: \goto{\hyphenatedurl{http://www.moderneskoeln.de/Die PROJEKTE/9 SIEBEN.htm}} [url(http://www.moderneskoeln.de/Die PROJEKTE/9 SIEBEN.htm)] [Accessed January 10, 2011]. \nl%
%
HGK, 2010c. Wohnwer[f]t 18.20. {\em Modernes Köln}. Available at: \goto{\hyphenatedurl{http://www.moderneskoeln.de/Die PROJEKTE/13 WW.htm}} [url(http://www.moderneskoeln.de/Die PROJEKTE/13 WW.htm)] [Accessed January 10, 2011]. \nl%
%
Hogan, J.P., 2006. The Politics of Urban Regeneration. {\em Progress in Irish Urban Studies}, 2, 27-37. Available at: \goto{\hyphenatedurl{http://www.fius.ie/Documents/Jhogan_PIUS_Vol.2.pdf}} [url(http://www.fius.ie/Documents/Jhogan_PIUS_Vol.2.pdf)] [Accessed December 20, 2010]. \nl%
%
Höhmann, I., 2010. Rheinauhafen Köln: Vorzeigequartier wartet auf Anschluss. {\em Wohnen - Immobilien - FAZ.NET}. Available at: \goto{\hyphenatedurl{http://www.faz.net/s/Rub8E0FC0CD826A4ACA80504FD9153A70F2/Doc\~E0CB48A76EDA6434784B7C3A44126DEEA\~ATpl\~Ecommon\~Scontent.html}} [url(http://www.faz.net/s/Rub8E0FC0CD826A4ACA80504FD9153A70F2/Doc\~E0CB48A76EDA6434784B7C3A44126DEEA\~ATpl\~Ecommon\~Scontent.html)] [Accessed January 11, 2011]. \nl%
%
Holm, A., 2010. „Recht auf Stadt“ – Mehr als ein guter Slogan? {\em hEft, für literatur, stadt und alltag}, (21), 32-33. Available at: \goto{\hyphenatedurl{http://heft-online.de/index2.php?option=com_docman&task=doc_view&gid=28&Itemid=65}} [url(http://heft-online.de/index2.php?option=com_docman&task=doc_view&gid=28&Itemid=65)] [Accessed July 19, 2010]. \nl%
%
immonet, 2010. Maritimes Wohnen im exklusiven Kranhaus im Rheinauhafen Köln, {\em immonet}. Available at: \goto{\hyphenatedurl{http://www.immonet.de/nordrhein-westfalen/koeln-innenstadt-altstadt-sued-etagenwohnung-mieten-10282d1217-1.html}} [url(http://www.immonet.de/nordrhein-westfalen/koeln-innenstadt-altstadt-sued-etagenwohnung-mieten-10282d1217-1.html)] [Accessed January 10, 2011]. \nl%
%
IVV, 2008. Eine "weiße Wanne" gegen Hochwasser: die RVG sorgt für Lebens- und Wohnqualität am Rheinauhafen. {\em Wohnraum}, (11), 18-19. Available at: \goto{\hyphenatedurl{}} [url()] [Accessed December 20, 2010]. \nl%
%
Kalkavan, Z., 2010. Port renovation projects fuel real estate boom in Galata. {\em Today's Zaman}. Available at: \goto{\hyphenatedurl{http://www.todayszaman.com/news-224611-port-renovation-projects-fuel-real-estate-boom-in-galata.html}} [url(http://www.todayszaman.com/news-224611-port-renovation-projects-fuel-real-estate-boom-in-galata.html)] [Accessed January 11, 2011]. \nl%
%
Kipfer, S., 2008. {\em How Lefebvre Urbanized Gramsci: Hegemony, everyday life, and difference}. In  New York: Routledge, pp. 193-207. \nl%
%%
Kipfer, S., Goonewardena, K. et al., 2008. {\em On the production of Henri Lefebvre}. In  New York: Routledge, pp. 01-16. \nl%
%%
Kipfer, S., Schmid, C. et al., 2008. {\em Globalizing Lefebvre?}. In Space, Difference, Everyday Life: Reading Henri Lefebvre.  New York: Routledge, pp. 285-301. \nl%
%%
Lefebvre, H., 1968. {\em Le Droit a la ville 1. ed.}, Paris: Anthropos. \nl%
%%
Lefebvre, H., 1974. {\em Le droit à la ville suivi de Espace et politique 1. ed.}, Paris: Anthropos. \nl%
%%
Lefebvre, H., 1970. {\em Le Manifeste différentialiste}, Gallimard. \nl%
%%
Lefebvre, H., 2008. {\em Space, difference, everyday life : reading Henri Lefebvre}, New York: Routledge. \nl%
%%
Lefebvre, H., 1991. {\em The production of space}, Oxford  OX  UK ;;Cambridge  Mass.  USA: Blackwell. \nl%
%%
Lefebvre, H., 1996. {\em Writings on cities}, Cambridge  Mass  USA: Blackwell Publishers. \nl%
%
Les Cahiers, 2007. {\em Large Scale Urban Development Projects in Europe: Drivers of Change in City Regions}, INSTITUTE FOR URBAN PLANNING AND DEVELOPMENT OF THE ÎLE-DE-FRANCE REGION. Available at: \goto{\hyphenatedurl{http://www.iau-idf.fr/fileadmin/Etudes/etude_469/c146_gb.pdf}} [url(http://www.iau-idf.fr/fileadmin/Etudes/etude_469/c146_gb.pdf)]. \nl%
%
Lopes de Souza, M., 2010. Welches Recht auf welche Stadt? Ein Plädoyer für politisch-strategische Klarheit. {\em Phase 2}. Available at: \goto{\hyphenatedurl{http://phase2.nadir.org/rechts.php?artikel=786&print=}} [url(http://phase2.nadir.org/rechts.php?artikel=786&print=)] [Accessed July 19, 2010]. \nl%
%
Marques, G., 2010. Pau e Circo: Copa, Olimpíadas, Movimentos Sociais e Cidade. Available at: \goto{\hyphenatedurl{http://pelamoradia.files.wordpress.com/2010/10/pau-e-circo.doc}} [url(http://pelamoradia.files.wordpress.com/2010/10/pau-e-circo.doc)] [Accessed January 11, 2011]. \nl%
%
Marshall, R., 2001. {\em Waterfronts in post industrial cities}, London ;;New York: Spon Press. \nl%
%
Niedt, C., 2006. Gentrification and the Grassroots: popular support in the revanchist suburb. {\em Journal of Urban Affairs}, 28(2), 99-120. Available at: \goto{\hyphenatedurl{http://www.hofstra.edu/pdf/Academics/css/css_jua_niedt.pdf}} [url(http://www.hofstra.edu/pdf/Academics/css/css_jua_niedt.pdf)] [Accessed December 20, 2010]. \nl%
%
Pesch, M., 2002. eine Marina in Köln...... KAMC - BOOTE-Forum. {\em KAMC}. Available at: \goto{\hyphenatedurl{http://forum.boote-magazin.de/showthread.php?t=17392}} [url(http://forum.boote-magazin.de/showthread.php?t=17392)] [Accessed January 10, 2011]. \nl%
%
Prigge, W., 2008. {\em Reading the Urban Revolution}. In Space, Difference, Everyday Life: Reading Henri Lefebvre.  New York, Abingdon: Routledge, pp. 46-61. \nl%
%
Purcell, M., 2002. Excavating Lefebvre: The right to the city and its urban politics of the inhabitant. {\em GeoJournal}, 58(2/3), 99-108. Available at: \goto{\hyphenatedurl{http://www.springerlink.com/content/m1856v64454767j9/}} [url(http://www.springerlink.com/content/m1856v64454767j9/)] [Accessed November 14, 2010]. \nl%
%
Rio Prefeitura \& CDURP, 2010. {\em Porto Maravilha}, Rio de Janeiro: Rio Prefeitura. Available at: \goto{\hyphenatedurl{http://www.portomaravilhario.com.br/media/informativo/boletim_do_porto.pdf}} [url(http://www.portomaravilhario.com.br/media/informativo/boletim_do_porto.pdf)] [Accessed January 10, 2011]. \nl%
%
RVG, 2010a. Büro \& Business im Rheinauhafen Köln. {\em Rheinauhafen Köln}. Available at: \goto{\hyphenatedurl{http://www.rheinauhafen-koeln.de/Business_Blaue_Seiten}} [url(http://www.rheinauhafen-koeln.de/Business_Blaue_Seiten)] [Accessed January 11, 2011]. \nl%
%
RVG, 2010b. Das Konzept des Rheinauhafens. {\em Rheinauhafen Köln}. Available at: \goto{\hyphenatedurl{http://www.rheinauhafen-koeln.de/Konzept}} [url(http://www.rheinauhafen-koeln.de/Konzept)] [Accessed January 10, 2011]. \nl%
%
Sassen, S., 1994. {\em Cities in a world economy}, Thousand Oaks  Calif.: Pine Forge Press. \nl%
%
Sassen, S., 1991. {\em The global city : New York, London, Tokyo 1. ed.}, Princeton  N.J.: Princeton University Press. \nl%
%
Shafik, R. \& Steele, J., 2010. {\em Tensions and Transformations in the Master Planning Process of Istanbul}. In Urban Transformation: Controversies, Contrasts, and Challenges. 14th IPHS CONFERENCE.  Iszanbul. Available at: \goto{\hyphenatedurl{}} [url()] [Accessed January 5, 2011]. \nl%
%
da Silva, C., 2009. As ocupações de prédios vazios e o esvaziamento do centro da cidade do Rio de Janeiro. {\em ChiqdaSilva}. Available at: \goto{\hyphenatedurl{http://www.chiqdasilva.com/site/index.php?option=com_content&view=article&id=56:imgtxt01&catid=3:textos&Itemid=4}} [url(http://www.chiqdasilva.com/site/index.php?option=com_content&view=article&id=56:imgtxt01&catid=3:textos&Itemid=4)] [Accessed November 5, 2010]. \nl%
%
Stanek, L., 2008. {\em Space as Concrete Abstraction: Hegel, Marx, and modern urbanism in Henri Lefebvre}. In Space, Difference, Everyday Life: Reading Henri Lefebvre.  New York: Routledge, pp. 62-76. \nl%
%
Statistikamt Nord, 2007. Hamburger Stadtteil-Profile 2007 für die neuen Stadtteile: HafenCity, Hammerbrook, Sternschanze. Available at: \goto{\hyphenatedurl{}} [url()] [Accessed January 5, 2011]. \nl%
%
Statistikamt Nord, 2008. Hamburger
Stadtteil-Profile 2008 NORD.regional Band 5. Available at: \goto{\hyphenatedurl{}} [url()] [Accessed January 5, 2011]. \nl%
%
Stredich, 2010. Tiefgarage Rheinauhafen, Köln. Available at: \goto{\hyphenatedurl{}} [url()] [Accessed January 5, 2011]. \nl%
%
STUDIOSarchitecture, 2010. Galata Port. {\em STUDIOSarchitecture}. Available at: \goto{\hyphenatedurl{http://www.studiosarchitecture.com/projects/65}} [url(http://www.studiosarchitecture.com/projects/65)] [Accessed January 11, 2011]. \nl%
%
Surborg, B., VanWynsberghe, R. \& Wyly, E., 2008. Mapping the Olympic growth machine. {\em City}, 12(3), 341-355. Available at: \goto{\hyphenatedurl{http://iocc.ca/documents/MappingTheOlympicGrowthMachine.pdf}} [url(http://iocc.ca/documents/MappingTheOlympicGrowthMachine.pdf)] [Accessed December 4, 2010]. \nl%
%
Tan, P., 2009. Istanbul: Widerstand im Stadtteil und gegenkultureller Raum. {\em Grundrisse}, (30). Available at: \goto{\hyphenatedurl{http://www.grundrisse.net/grundrisse30/Widerstand_im_Stadtteil.htm}} [url(http://www.grundrisse.net/grundrisse30/Widerstand_im_Stadtteil.htm)] [Accessed January 11, 2011]. \nl%
%
Tan, P., 2007. Spatiality, Resistance and the Production of Locality. \nl%
%
Taylor, P.J., 2009. {\em Measuring the World City Network: New Results and Developments}, Loughborough: GaWC. Available at: \goto{\hyphenatedurl{http://www.lboro.ac.uk/gawc/rb/rb300.html}} [url(http://www.lboro.ac.uk/gawc/rb/rb300.html)] [Accessed December 3, 2010]. \nl%
\stopREF%
}

\stopenvironment