\startcomponent component_NarratingInquiries_SaoPauloDiaries_DayAndNight
\product product_Thesis
\project project_MasterThesis

% definitions and macros
\environment envThesisAllEnvironments
\environment envCfgThesisImages 

\define[]\subsectionSaoPauloDiariesDayAndNight{\subsection[narratinginquiries_saopaulodiaries_dayandnight]{Day//Night//Streets}}

\define[]\subjectDayOne{\subject{Day//One}}
\define[]\subjectNightOne{\subject{Night}}
\define[]\subjectDayTwo{\subject{Day//Two}}
\define[]\subjectDayTwoCondepe{\subject{CONDEPE}}

\starttext

\startmode[tocLayout]
\subsectionSaoPauloDiariesDayAndNight
The section is a narrative of two days and a night experience on the streets of São Paulo.
\subjectDayOne
Introduction to several spots in the centre.
\subjectNightOne
Looking for a place to sleep.
\subjectDayTwo
Visiting more places, a emergency case 
\subjectDayTwoCondepe
the final visit of CONDEPE.
\stopmode

\startmode[draft]
\subsectionSaoPauloDiariesDayAndNight
Today, \Ma and I are going to realize I our two days journey on the streets. We meet at \Ay, its early in the afternoon. \Ma intention is to introduce me to the lived space of the people in street situation, that I experience how to organize daily life on the streets, how people support each other and how people are adversely affected by public policies, institutions and agents.

\spaceHalf

\inright{heavy rain and its effect on the streets}
This week São Paulo is going to be \aLinkMediaNew[hit by a cold weather front]{http://bit.ly/mQxbEJ}\toMark{13/07/2010}. It is already cold today, probably 15 to 20 degrees during the day but at night, temperature will drop to 10 to 12 degrees. It will start to rain as well.

Some days later heavy rain is basically stopping the movement in the city for one week. \aLinkMediaNew[Newspapers report impassable roads]{http://bit.ly/nrKPY7} \toMark{14/07/2010} caused by floods throughout the city.

\startPersonal
The cold weather has severe effects on the movement of the people on the streets. Those that are in streets situation will leave the lower places of the centre in order ascend the steep hills up to\locAvPaulista. Looking at the city topographically, \Se or \Republica are located in the valleys of the surrounding hills. Once heavy rain hits the city, those lower places are much more prone to floods then the upper areas on the hills, where \AvPaulista is located for instance. Thus heavy rains forces people to leave the lower areas and ascend upwards in order to avoid being flooded away and in order to find a more or less secure and dry place to sleep. 

Even though those urban floods are not comparable to river floods, during the period of heavy rain small rivers pop up everywhere on the side walks and the streets because the city is sealed by constructions and water is searching its way wherever possible, accumulating in streams that make it impossible to sleep on the ground. 
\stopPersonal

\subjectDayOne

But for now, we start our journey downwards, descending \aLocationNew{Rua  Carmelias}{http://osm.org/go/M@ziKy3jL--} until it hits \aLocationNew{Rua Frederico Alvarenga}{http://osm.org/go/M@ziK8Ucu--}. There, at the corner we meet one of \Mas friends. He is sitting there at the corner most of the day, almost everyday. Right now he is sleepy and does not talk much. We do not stay long, \Ma is just asking how his friend is doing and then we continue. \Ma says that he knows him since he hits the streets, years back, and since then the guy always stayed at that corner every day. 

We are heading towards the \Tendas. They are not far away, just two streets, located below \aLocationNew{Viaduto 25 de Marco}{http://osm.org/go/M@ziLozVF--} where \aLocationNew{Avenida Rangel Pestana}{http://osm.org/go/M@ziLozVF--} traverse a branch of \aLocationNew{Rio Tietê}{http://osm.org/go/M@zie@K}\aLinkNewF[Rio Tietê at Wikipedia]{http://bit.ly/pvlcQg} that crosses through the northern part of the city's central area.

\spaceHalf

\inright{loosing means to generate income}
We arrive at the junction where \aLocationNew{Rua Dom Pedro II and Avenida Rangel Pestana}{http://osm.org/go/M@ziK3nYF--} are crossing and meet another friend of \Ma. He tells us that the \abbr{GCM} has just taken all his possessions, his bag and all the goods he was selling on the streets because he could not show a permission as street vendor when \abbr{GCM} has been checking him. Thus he has just lost all means to generate income.

\spaceHalf

\inright{entering the Ţendas}
We cross the street and entering the \toTranslate[Tendas]{tents}. \Tendas is the name of an area converted to a public service that receives people in street situation. The \toTranslate[Tenda de convivência]{Tenth of gathering} at Parque Dom Pedro is a service provided by the Secretaria Municipal de Assistência Social of the Prefeitura de São Paulo \aLinkNewF{http://bit.ly/qImvjC}.

The \Tendas at Parge Dom Pedro consists basically of a huge tent, open to one side, packed with people sitting on banks and chairs, in front of a TV. The backmost part is occupied for showers and toilets. Outside the big tent, groups of people are sitting everywhere, some of them talking, some just quite. The atmosphere is rather depressed. We talked to a social worker who told us that they are also offering workshops from time to time, such as \toMark{nochmal in meine aufzeichnungen schauen}. The \Tendas are open during the day from 8h in the morning until 9h in the evening and closed for the night.  

\startARemark{woher kommen die leute nochmal? alberque oder strasse oder beides?}\stopARemark
\startARemark{mehr über die tendas in meinen aufzeichnungen}\stopARemark

\startPersonal
The \Tendas are located at a spot of the centre that is usually not much frequented, except by cars that rush over the three lane avenue that is passing above them in order to traverse the river. It is noisy and the air is polluted by massive traffic that is circulating all day long from the centre to the eastern regions of São Paulo and vice versa. The traversals at\locParqueDomPedro, thus above the \Tendas, eventually connect the centre with Brás and the \aLocationNew{Radial Leste}{http://osm.org/go/M@zoEwXb-} highway that head towards the eastern margins of the city. 

Especially the notion of artesian workshops becomes contradictory when we thought about the friend we met just before, who is actually living from vending artesian goods on the streets and who has been expelled by the police for doing so. 
\stopPersonal

According to \Ma, the\Tendas are just another way of keeping people in their miserable situation because they do not provide a  single proposal to sustainably improve the situation of the people. For \Ma they are solely a justification for public institutions, civil and police agents, to banish people from the central commercial areas and send them here because the city wants clean the commercial centre of all unwanted subjects. What awaits them at the \Tendas is the just a TV, some workshops, food and sanitation. \Ma said that the chemical sanitation is dirty like hell and that he would not take a shower here anyway.

\startDialog
\tell{\Ma}{Look what people can do here. Nothing. They just sit in front of the TV all day long and wait until the place closes its doors at night. Tomorrow they will be here again but how can they improve their situation then?}
\stopDialog

\spaceHalf

\inright{heading towards Sé}
We leave the the \Tendas after a while and head towards \Se. \Ma says that a research has been released at the end of last year \bracket{2009} which determines the number of people in street situation in São Paulo between 13000 und 14000. He says that this number is way to low. According to the estimation of the very people on the streets, the number of could be between 20000 and 25000. 

\spaceHalf

\inright{official census about people in street situation}
The study conducted by \abbrNew{Fundação Instituto de Pesquisas Econômicas}{FIPE} \toTranslateT{Fundação Instituto de Pesquisas Econômicas}{Institute of Economic Studies Trust} says that 13666 people in São Paulo are considered being in street situation, half of them staying in \Albergues \bracket{7079}, the other half staying on the streets \bracket{6587} \aQuoteB{Schor and da Costa Vieira}{2009}{4} \footnote{ \abbr{FIPE} is private not-for-profit institute that supports research of the Faculty of Economy, Administration and Accountancy of the University of São Paulo (FEA-USP) (\aLinkNewNoF[O que é a Fipe]{http://bit.ly/rlQyOQ})}.

\startARemark{\Ma complains that those numbers are wrong}
because....
\stopRemark

\startDialog
\tell{\Ma}{You know what? Albergues are like human deposits. You have to wake up at 5 o'clock in the morning, you get a coffee and then they kick you out. You can only come back at night, punctual, depending on the place you are. Sometimes at 9 p.m sometimes later. The only thing you do there is sleeping. You cannot leave your stuff there because others will steal it and they don't allow you to keep your stuff there. There is nothing where you can deposit your stuff. And can you imagine that people stealing from others in the same situation?}
\tell{\Ma}{Sometime pereople make noise all night long, how can you sleep then? If you don't obey the rules they kick you out immediately, its like prison in there, but imagine people that lived on the streets for 10 years or so, how can one force them to obey those rules? Their life on the streets changed their behaviour, you cannot force them to follow rules that did not exist on the streets. I preferred to stay on the streets instead of being \quote{home} punctual, leaving my ID there and always being afraid that someone will come to take my stuff away. Its a human deposit. People are not empowered there, they are just taken from the streets for the night but left in their miserable situation. During the day you have to hit the streets anyway. Then people are just waiting to get back at night, that's all what happens when you go to the Albergue. It doesn't change anything.}
\tell{\Ma}{And how can it? Albergues are packed up. Mostly men are received there, a few of them are for mixed gender or families. But men and women are then always separated strictly. An what does the Prefeitura? They even close Albergues, alone last year \toMark{X} of them have been closed, all together about \toMark{1200} places, \toMark{X at Y, X at Y and X at Y}. One of them, Cirineu is located to the opposite of the Camerá Municipal. The politicians did not want to see the miserable reality in front of their faces so they just closed it. When new Albergues are inaugurated they are far away from the centre. People have to take public transport there, \toMark{for example to} and once they are there they won't come back to the centre because there is no work for them, their social network is not function there, as is does here in the centre and if they can't earn money they can't afford public transport back here. Its a convenient way for the city to expel people from the central areas and clean them up as positive side effect.}
\tell{\Ma}{Let's go there to Cirineu there at the Camerá Municipal, the one they closed some month ago, eliminating \toMark{X places}}
\stopDialog

So we are heading to the \aKeyword[Cirineu]{streets+places+institutional+albergue+Cirineu}, the \Albergue opposite to the \toTranslate[Camara Municipal]{Municipal Chamber} at the corner of \aLocationNew{Viaduto Jaceguai and Rua Santo Amaro}{http://osm.org/go/M@ziIyW@E--}. 

We flow through the centre meeting people at every corner. The centre is the lived space that \Ma knows inside out. Literally every corner, every small street, every blind, wall, canopy, roof and loophole that protects from rain, wind and that protects one self from others. \Ma says that he never slept alone, they always stayed in small groups, with his \aKeyword[familía]{streets+actors+streets+família} that meant protection and reliance. 

Here a street where \Ma slept with others for three years under a shop's canopy, every night until the place was secured with a lattice so that no one could sleep there any more once the shop closed its doors in the evening and the lattice shielded the canopy. 

We already crossed \aLocationNew{Viaduto do Chá}{http://osm.org/go/M@ziJvMDT--} and enter \aLocationNew{Rua Barão de Itapetininga}{http://osm.org/go/M@ziJ5YHu--} where we meet another friend of \Ma with his wife. This friend is not in street situation but works as a social worker for the public service whose agenda are the people in street situation. He tells us that he just has quit his job at the service because it was no longer possible for him to support what has been required from him in terms of forcing people away from the streets. \Ma and he are talking a long time because they have not seen each other for month. 

Then we leave them and turn to \aLocationNew{Anhangabaú}{http://osm.org/go/M@ziJpyD2--} and from there towards \aKeyword[Cirineu]{streets+places+institutional+albergue+Cirineu}, floating through the overground pedestrian way connecting the centre with the bus terminal \aLocationNew{Terminal Bandeira}{http://osm.org/go/M@ziI9Gin--}. Here the same picture, everywhere friends and known faces \Ma is acquainted with, sitting in between the constant stream of people heading to the metro stations, the bus terminals or elsewhere. 

From there we are climbing up the road to \aLocationNew{Viaduto Jaceguai }{http://osm.org/go/M@ziIyW@E--}. Its getting dark, must be around 7 p.m. We just take a look at the place, there is not much to see, just the history is important. We continue, \Ma would like to show me one of those \Albergues that receives families and mixed gender. Its located at \aLocationNew{Rua São Domingos}{http://osm.org/go/M@ziIlROe--}. At the entrance just an old woman waiting to get inside. We are staying here just a short while. 

It is already dark now and the area is shady so we decide to return to the centre, to  \aLocationNew{Praca Ouvidor Pacheco e Silva}{http://osm.org/go/M@ziI@zJh--} for a short break and for organizing something to eat. Once we arrived there we are already 4 or 5 hours floating through the area.

\startDialog
\tell{\Ma}{Do you see how the city is constructed. Look here, do you see this walls? They shield the ventilators that are blowing warm air from the inside of the building. The shop just constructed those walls because people were sleeping on the lattices above the ventilation system. There has always been a warm stream of air. Especially with temperatures like today you would have seen the lattices full of people because its the only warm place here outside. Now they put those walls there to prevent that have an incentive to come and stay here. They think its not good for their business, but look, there so many people still sitting here and freezing today.}
\tell{\Ma}{And have you seen those shops on the opposite of the Faculty of Rights? They installed those massive lattices there to prevent people to sleep below their canopies. But this is public space, they privatized public space by making it inaccessible and try to draw us out from here by preventing us to stay in areas that protects. And the Prefeitura is happy because now this private shop owners are doing the dirty business of installing stuff that is supposed to make our life even more difficult. The Prefeitura does not even need to do this because the people are doing it already. There at Sé you have already seen that the cathedral is entirely fenced. They fence a church that is supposed help everyone. Its a property of the church but this church is as worse as the Prefeitura. They only care about the tourists coming there to shoot photos but what is with those that used to sleep there, at those walls?}
\stopDialog

\imgPanoramaSe

\startDialog
\tell{\Ma}{You see, the centre used to support us in our daily struggle but now there is not even water in the dwells at Sé or República and only one public toilet in the whole area. We will go there tomorrow morning after we woke up. The city is ripped off every infrastructure that supported us. Have you seen benches somewhere? If there are benches they are too narrow to sleep on them. But most of the public spaces do not have any bench, and where are we supposed to wash our self or go to toilet. The public opinion is that we piss everywhere but what would you do without toilet living on the streets. And even to the bars you cannot go because you can use their toilets only if you buy something. Every citizens is struck by this situation but we are the guilty ones.}
\stopDialog

\Ma says we have to wait until 9 p.m. because then \aKeyword[citizens]{streets+actors+groups+citizens} and \aKeyword[Grupos de Sopa]{streets+actors+groups+grupo de sopa}\toTranslateT{Grupos de Sopa}{Soup Kitchen} will arrive and distribute food. Till then we sit here on a low wall, around us other people, mostly men, waiting for the arrival of food. Its cold, we are freezing.

\Ma says that when you life on the street you need to learn from where you can get food for free, without money. Water is another problem because there are no public wells left in the centre, thus those that distribute food mostly also bring water. The distribution takes place at different spots in the central area, often in the evening. 

There are other places such as courtyard of an \aKeyword[abandoned villa]{streets+places+abandoned+villa} alongside the \Minocao at\locRuaApa\footnote{\Minocao is the name of the elevated highway Presidente Costa e Silva and covers a large extend of \locAvSaoJoao, leading from the centre to the West, to \locBarraFunda. Some impressions of the \Minocao can be found at \aLinkNewNoF[Minhocão, 24 horas]{http://blogs.estadao.com.br/olhar-sobre-o-mundo/minhocao-24-horas/}. The Minhocão is open for traffic during the day but is closed at night and on Sundays all day long. There is much to say about that street, but this has to wait till another time.}. \Ma says that the people in street situation below the Minhocão are separated from those of the centre but also from those at Luz, they do not have much contact. We decide to go to Luz later on but that we spare \Minocao for tonight. 

\startPersonal
I perceived the \Minocao as even rougher then the centre. It is hard for me to say, its probably the heavy car traffic and those traffic jams all day long, the pollution, the noise. Even it is not that long from the centre, its a different world already. I had never contact with people living there and those I met in the centre never went there as well.
\stopPersonal

Around 9 p.m. the first van is entering the pedestrian area around \locOuvidorPacheco. Its a van of a \aKeyword[Grupo de Sopa]{streets+actors+groups+grupo de sopa}. They stop and one guy on top of the bed is distributing half litre plastic bottles of water to everyone that is approaching the van. \Ma and I are taking two because we didn't drink since the afternoon. We also get some bred and returning to our place. \Ma says 

\startDialog
\tell{\Ma}{Look how fast everything goes. They are not allowed any more to do this here.}
\stopDialog

After some minutes the van has nothing left and is leaving the area. On the opposite of the place, another car is stopping, this time a father with his two kids. He opens the trunk of his car and takes out boxes with cups of warm food. The movement of the people is starting again. The family is passing the plastic cups with warm noodles, sauce and some meat to everyone. \Ma says that this family is doing this every week, always on the same day, at the same time. We talk with them shortly before they leave and they say that they had prepared around 80 portions at home for tonight. As fast as they arrived they leave. Their portions are distributed fast as well and within a couple of minutes all cups are gone. \Ma says that those that do not go to the \Tendas or the \Refeitorios have now probably got their first and last meal of the day.

\startPersonal
I feel a bit strange not eating the meat in my sauce but I leave it for \Ma.  I would never complain about it because we were both hungry and no one would throw away stuff the other could eat. It is ridiculous to prohibit the self-organisation of food distribution. That people freely organise the distribution implies that they care about the situation in the city and that their practice is pragmatic and self-determined. They simply come to the place where the people are. Nothing more and nothing less.
\stopPersonal

\startARemark{some days later I found several newspaper articles about the same topic.} They are arguing from the standpoint of the owners of commercial businesses in the central areas and from the standpoint of the cities public agents.

übersicht hier hin und nochmal auf die tendas eingehen.

\stopARemark

Seeing the car leaving we are also leaving the place, saying goodbye to everyone around us and heading towards \Republica.

%\reference[narratinginquiries_daysandnight_pressalberques]{}
%\startPressCoverage{Press coverage about the issues of shutting down Albergues in central areas.}
%\tellPress{}{}
%\tellPress{}{}
%\tellPress{}{}
%\stopPressCoverage

%\reference[narratinginquiries_daysandnight_presssopatendas]{}
%\startPressCoverage{Press coverage about the tendas and food distribution.}
%\tellPress{}{}
%\tellPress{}{}
%\tellPress{}{}
%\stopPressCoverage

%\reference[narratinginquiries_daysandnight_pressfipe]{}
%\startPressCoverage{Press coverage about the census conducted by FIPE.}
%\tellPress{}{}
%\tellPress{}{}
%\tellPress{}{}
%\stopPressCoverage

\subjectNightOne
\reference[narratinginquiries_saopaulodiaries_dayandnight_lookingforaplacetosleep]{}Looking for a place to sleep.

\subjectDayTwo
Visiting more places, a emergency case and the final visit of CONDEPE.

\subjectDayTwoCondepe

Finally we terminated our journey at the \aLinkNew[CONDEPE-SP]{http://www.condepe.org.br/conheca/} which took place at \aLinkNew[Espaço da Cidadania]{http://www.justica.sp.gov.br/novo_site/} \quote{André Franco Montoro}, located at \aLocationNew[Largo Pateo do Collegio, 184]{http://osm.org/go/M@ziLLCwJ--}, right besides \Se. Its around 3 o'clock in the afternoon.

The \abbrNew{Conselho Estadual de Defesa dos Direitos da Pessoa Humana}{CONDEPE} \toTranslateT{Conselho Estadual de Defesa dos Direitos da Pessoa Humana}{the states council for the protection of the rights of the human being} is a public institution composed of representatives of the civic society and public authorities whose aim is to

\startCitation
Investigate violations of human rights on the territory of the state São Paulo, forward denunciations and representation to the corresponding and competent authorities and to study and propose general solutions for the related problems, in order to protect the basic rights of the human being. \aQuoteW{CONDEPE}{2011}
\stopCitation

This Thursdays council has been a special public audience in certain ways: several women of the \aLinkNew[Mães de Maio]{http://maesdemaio.blogspot.com/} publicly demanded the clearing of the executions of their children in May 2006 which has been supposedly conducted by assassination squads that existed and presumably still exist within the \abbrFull{PM}. The victims were predominantly \toTranslate[jovens negros]{black kids}, afro-indigenous-descendants and poor, who lived in the peripheries of ﻿Baixada Santista, the metropolitan region that surrounds the city of Santos, on the coast of the state of São Paulo.

\startCitation
We are mothers, family members and friends of the victims of state violence (primarily police), that came together at the begin of the notorious Crimes of May 2006 [...] During May 2006, police and paramilitary assassination squads caused one of the most shameful scandals in the history of Brazil. In a cynic and mendacious \aLinkNew[wave of responses]{http://www.midiaindependente.org/pt/red/2006/05/353903.shtml} at the so called „attacks of the \abbrFull{PCC}" as they have been referred to by the big media, at least 493 persons were assassinated – today considered either dead or missing. The great majority – more then 400 black kids, afro-indigenous-descendants and poor – basically executed. Without doubt is this the major and most symptomatic massacre in recent Brazilian history. \aQuote{Mães de Maio}{2010}
\stopCitation

\imgMaisDeMaioCondepe

The fact that the majority of the victims have been black kids, raised the general criticism of institutional racism against poor and predominantly black Brazilian citizens, here with respect to racial motivated police violence. The assassinations of May 2006, \aLinkNew[the killing of two black motoboys]{http://bit.ly/b00jg6}\aQuote{Azevedo and Leão}{2010} in 2009, the \aLinkNew[Operacão Saturacaõ]{http://www.midiaindependente.org/eo/blue/2006/09/361301.shtml}\aQuote{D.A}{2006} in \aLinkNew[Jardim Paraisopolis]{http://passapalavra.info/?p=643}\aQuote{Passa Palavra}{2009} in 2009 and the \aLinkNew[most recent attacks]{http://glo.bo/nzJpnE}\aQuote{Stochero}{2010} at the \abbr{Rota} which resulted in \aLinkNew[36 death in the first days after the attack]{http://miseriahq.blogspot.com/2010/08/rota.html}\aQuote{MISÉRIA}{2010}, have been exemplary cited by black/afro and social movements in their open letter to CONDEPE and the people of São Paulo. In this letter, several movements and groups demand the immediate dismissal of the Secretary of Public Security, Antonio Ferreira Pinto and the Colonel General of the \abbr{PM}, Álvaro Camilo.

During the audience, a vast variety of reports have been given on the attacks in May 2006. Several women of Mães de Maio talked about the death of their children and heavily criticized that most of those cases, after 4 years, are still not clarified.

\aLinkNew[A reporter from Santos]{http://bit.ly/oYd2IG}\aQuote{Sindicato dos Jornalistas}{2010} spoke about his investigations that have been published in the newspaper \aLinkNew[O Tribunal de Santos]{http://infanciaurgente.blogspot.com/2010/04/4-anos-dos-crimes-de-maio.html}\aQuote{Santana}{2010} in which he showed that assassination squads exist within the Polícia Militar, and that those groups carried out the assassinations in 2006 and presumably more in the following years.

A representative of the \abbr{MNPR} spoke about the notorious (police) violence against the the city’s streets inhabitants and emphasized their very vulnerable living conditions, which means that people die unidentified after attacks due to the fact that many of them don’t possess papers.

The secretary of the Department of Public Security was invited as well but didn’t show up but sent instead a representative which citied in his speech an internal report about the investigations on the attacks in May 2006. As a consequence a small number of police members have been detained. The representative heavily defended the “glorious” Policia Militar and tried to leave immediately after his speech, but several persons in the audience and the head of CONDEPE heavily criticized that public organs have been invited to listen to the victims of police violence, don’t show up personally but send representatives instead , which in turn don’t want to listen what citizens have to say. The representative was finally forced to stay despite other “important” dates.

The following excerpts are taken from the audio files that have been recorded during the audience. All records can be found on \aLinkNew[archive.org]{http://www.archive.org/details/CondepeSoPaulo_446}. The blog of the \aLinkNew[Mães de Maio]{http://maesdemaio.blogspot.com/2010/08/audios-da-audiencia-publica-do-condepe.html} and \aLinkNew[Passa Palavra]{http://passapalavra.info/?p=28579} also released articles about the CONDEPE and linked to the available audios. Cool!! 

Ivan Seixas – Head of CONDEPE
\startCitation
[...] the dead of Christiano is a symbolic case for us [...] a poor citizen, a black citizen, a young boy, a worker, is not supposed to die [...] if he was a criminal, even if he was a criminal, he was not supposed to be executed [...]
\stopCitation

Doutor Márquez de Rivera – presents statistics of killed persons due to police violence in the state/the city of São Paulo from 2004 to 2009

\startCitation
[...] who works in this area of human rights since many years and who will talk about a very dangerous development which is an engagement to assassinations, to massacres, that happen in the city of São Paulo [...]
\stopCitation

Ivan Seixas – talks about the numbers of death of a civil war

\startCitation
[...] its not normal to kill, we were not programmed to kill, the police is not programmed to kill, not prepared to kill, this is fundamentally important for us [...] the numbers of a civil war in a city, in a state like we have here are shocking,, are alarming, we have to do something [...]
\stopCitation

Ivan Seixas – talks about assassination squads within the Polícia Militar

\startCitation
[...] this is extremely severe for us, extremely severe, because it became evident due to a series of articles published in the newspaper of Santos, that the group is an assassination squad, which is formed with the declared intention to kill, and now, killing, they know who is going to die, who is a criminal, according to their definition [...]
\stopCitation

representative of  Movemento Nacional da Populacão de Rua

\startCitation
[...] in this data that was assembled, we don’t know for example if people from the streets were included., because persons from the streets who have no papers and ids and which are killed [...] are cases that nobody is looking at [...]
\stopCitation

Ivan Seixas – talks about the function of CONDEPE

\startCitation
[...] it is extremely important that the people understand what CONDEPE is, what its purpose is. CONDEPE is not an individual entity, it is composed of other entities and there exist no strong CONDEPE without strong entities. Now, this entities, they alone have not the power CONDEPE has, and which is available through CONDEPE to them, such as [...] the power to enter every unit of the state of São Paulo [...] to claim, to request documents, clarifications, informations, reports, from every entity of the state of São Paulo, from the government of the state of São Paulo [...] therefore it doesn’t make the slightest sense to stop [...] therefore I issue an invitation to all entities that are now present to use this instrument. We don’t receive anything for our work, our work is voluntary and is supposed to help the community. Every entity can participate in CONDEPE and can use it as instrument for actions [...]
\stopCitation

Condepe – some declarations

\startCitation
[...] we could debate with the state, not with the government – the government goes away, the state stays – debate with the public and police agents [...] in order to find alternatives that avoid or stop that large number of killings that occurs and push the people in the audience [...]
\stopCitation

Dona Christina – Mães de Maio – mother of Christiano, talks about the assassination of her son and the non existence of investigation

\startCitation
[...] I asked him – “you are leaving?” – and he said – “yes, just came back home to take my shoes” – [...] that was the last time I saw him. Afterwards I looked in all places, in the hospitals, nothing [...]
\stopCitation

The representative of the Antônio Ferreira Pinto – Secretary of Public Security

\startCitation
Ivan Seixas: “[...] I regret that you (the representative) have to leave, because, as always, we published a public invitation, invited all secretaries, and so on and so forth, and the secretaries don’t send their titleholders, but instead send representatives. And you came as representative but have to leave, without listening to the families that are going to talk [...] and exactly because of this, the titleholders don’t come, send representatives, the representatives have to leave immediately, i propose the following compromise: you are going to listen to the Defensoria Publica and afterwards, we are going to bring to the Secretary of Security, to the Secretary of Justice, to the Casa Civil, to the government, all the reports or claims, and the proposals, the many proposal that request the dismissal of the commander of the PM, the dismissal of the secretary of security, and we have to discuss this [...]”
\stopCitation

unknown speaker – a structural problem of police violence

\startCitation
[...] what is important for the government to admit is that there exist a problem with the police, not with one or another policeman. If it has been just one or another policeman, that problem would have been already resolved but as the numbers show, every year exist a larger and absolutely disproportional number of death's [...]
\stopCitation

Roseli de Oliveira – coordinates the Programa e Políticas para a População Negra e Indígena do Estado de São Paulo

\startCitation
[...] the question of racism is a structural problem, not only in the systems of police and justice, its a structural problem of the Brazilian society. [...]
\stopCitation

Mães de Maio

\startCitation
[...] we came from Baixada Santista, we didn’t come as tourists to São Paulo, we came to confront the state, the state has to give an answer to us about what happens in Baixada Santista [...]
\stopCitation

Flavia Gonzages – Mães de Maio – talks about the death of her son Marcus Paulo

\startCitation
[...] just one policeman arrested, its ridiculous, ridiculous. 23 killed in 3 days, and my son was right in the middle of them. He was no animal, he died like waste. I don’t have anything else to say, he died like waste [...]
\stopCitation

\addReference
{
CONDEPE, 2011. CONDEPE - SP. {\em CONDEPE - SP}. Available at: \goto{\hyphenatedurl{http://www.condepe.org.br/conheca/}} [url(http://www.condepe.org.br/conheca/)] [Accessed September 13, 2011].
}

\addReference
{
Schor, S.M. \& da Costa Vieira, M.A., 2009. Principais Resultados do Censo da População em Situação de Rua da Cidade de São Paulo. Available at: \goto{\hyphenatedurl{http://www.prefeitura.sp.gov.br/cidade/secretarias/upload/chamadas/2\_1275339508.pdf}} [url(http://www.prefeitura.sp.gov.br/cidade/secretarias/upload/chamadas/2_1275339508.pdf)].
}

\addReferenceMedia
{
Azevedo, S. & Leão, N., 2010. A tropa está fora de controle? {\em ISTOÉ Independente - Brasil}. Available at: \goto{\hyphenatedurl{http://bit.ly/b00jg6}}[url(http://bit.ly/b00jg6)] [Accessed August 23, 2010].
}

\addReference
{
D.A., 2006. Operação Saturação. {\em CMI Brasil}. Available at: \goto{\hyphenatedurl{http://www.midiaindependente.org/eo/blue/2006/09/361301.shtml}} [url(http://www.midiaindependente.org/eo/blue/2006/09/361301.shtml)] [Accessed August 23, 2010].
}

\addReference
{
Mães de Maio, 2010a. Audios da Audiência Pública do Condepe. {\em MÃES DE MAIO}. Available at: \goto{\hyphenatedurl{http://maesdemaio.blogspot.com/2010/08/audios-da-audiencia-publica-do-condepe.html}} [url(http://maesdemaio.blogspot.com/2010/08/audios-da-audiencia-publica-do-condepe.html)] [Accessed September 3, 2010].
}

\addReference
{
Mães de Maio, 2010b. Mães de Maio contra a violência do Estado. {\em Passa Palavra}. Available at: \goto{\hyphenatedurl{http://passapalavra.info/?p=28579}} [url(http://passapalavra.info/?p=28579)] [Accessed September 3, 2010].
}

\addReference
{
MISÉRIA, 2010. Mortes aumentam depois de ataques contra a Rota. {\em Revista Miséria}. Available at: \goto{\hyphenatedurl{http://miseriahq.blogspot.com/2010/08/rota.html}} [url(http://miseriahq.blogspot.com/2010/08/rota.html)] [Accessed August 23, 2010].
}

\addReference
{
Passa Palavra, 2009. A revolta de Paraisópolis para além dos fatos. {\em Passa Palavra}. Available at: \goto{\hyphenatedurl{http://passapalavra.info/?p=643}} [url(http://passapalavra.info/?p=643)] [Accessed August 23, 2010].
}

\addReference
{
Santana, R., 2010. 4 ANOS DOS CRIMES DE MAIO. {\em INFÂNCIA URGENTE!!!!!}. Available at: \goto{\hyphenatedurl{http://infanciaurgente.blogspot.com/2010/04/4-anos-dos-crimes-de-maio.html}} [url(http://infanciaurgente.blogspot.com/2010/04/4-anos-dos-crimes-de-maio.html)] [Accessed August 23, 2010].
}

\addReference
{
Sindicato dos Jornalistas, 2010. Jornalista que denunciou grupos de extermínio na Baixada Santista sofre ameaças. {\em www.sjsp.org.br}. Available at: \goto{\hyphenatedurl{http://bit.ly/oYd2IG}} [url(http://bit.ly/oYd2IG)] [Accessed August 23, 2010].
}

\addReferenceMedia
{
Stochero, T., 2010. Ataque à Rota pode ser vingança. {\em Diário de São Paulo}. Available at: \goto{\hyphenatedurl{http://glo.bo/nzJpnE}} [url(http://glo.bo/nzJpnE)] [Accessed August 23, 2010].
}

%---------------------------------------------------
% gets only displayed in unfinished mode

\showImperfection

%---------------------------------------------------
\stopmode

\stoptext

\stopcomponent