\startcomponent component_Theorizing_Outro
\product product_Thesis
\project project_MasterThesis

% definitions and macros
\environment envThesisAllEnvironments

\define[]\sectionOutro{\section[theorizing_outro]{Almost finished...?}}

\starttext

\startmode[tocLayout]
\sectionOutro

Final words about theoretical themes.

\stopmode

\startmode[draft]
\sectionOutro

\startARemark{Struktur und Inhalt des Theorizing Kapitels}
\stopARemark

\inright{\aKeyword[Citizenship]{theorizing+citizenship}}

\aQuoteB{Miraftab}{2006}{200}
Campaign activities try to ground the notion of citizenship as a practice, not
a given (Gaventa 2002: 4), the practice that Holston and Appadurai (1999: 2)
describe as aspiring to ‘new kinds of citizenship, new sources of laws, and new
participation in decisions that bind’. As a Campaign activist put it, important
as it is to establish relevant formal channels for making claims, the laws are
often ineffective and fall short of meeting the immediate needs of the poor
(Bobby Wilcox, paraphrased interview 2002).
We understand the limitation of the legal system. We can’t confine the struggle to
the legal system . . . [and have] the courts become the site of our struggle. Using
the court is one technique that we use, but it is not the most effective tactic. But
we’ll use it if there is space to use it in that case and at that level. But we need to
also realize that law keeps changing and [that laws] are more accessible to the
rich than the poor because they have more resources to access and to change
the law and poor people don’t have those kinds of resources. We are very
conscious about how we use the law and when we use the law.
(Faizel Brown, interview 2004)

\aQuoteB{Miraftab}{2006}{201}
But they try not to limit their struggle to any of those sites. When
formal channels fail, they innovate to create alternative channels and spaces
for active citizenship to assert their rights and negotiate their wants. They
use formal spaces when they are advantageous, and defy them when they
prove unjust and limiting.

\aQuoteB{Miraftab}{2006}{205}
By showing that formal and informal spaces are not self-contained sites
of politics but porous, each shaping the other (Hassim 1999: 12), feminist
scholarship in South Africa strengthens the more general feminist challenge
to binary constructs such as public/private and active/passive, and to the
traditional assumption that political participation and citizenship only takes
place in the sphere of formal politics dominated by men.


\aQuoteB{Arnstein}{1969}{216-224}\aQuoteInTextT{a Ladder of Citizenship Participation}

There is a critical difference between going through the empty ritual of participation and having the real power needed to affect the outcome of the process. 

The justification for using such simplistic abstractions is that in most cases the have-nots really do perceive the powerful as a monolithic "system," and powerholders actually do view the have-nots as a sea of "those people," with little comprehension of the class and caste differences among them.

citizenship exists only insofar as it is enacted, and its emerging figures have to do with empowerment strategies exercised in and from the cultural sphere. What the new social, ethnic, gender, gay and lesbian, religious or ecological movements demand is not only ideological representation but also socio-cultural recognition. They seek to become visible in their difference as citizens. This opens up a new mode for the political exercise of their rights, since this new visibility catalyzes the emergence of new political subjects. This was the subject visualized by feminism when it subverted the Left's profound machismo with its slogan: “the personal is political!” which came to embody both a sense of injury and victimization and a sense of recognition and empowerment.

\aQuoteW{Barbero}{20}\aQuoteInTextT{Staging Citizenship: Performance, Politics, and Cultural Rights}

citizenship exists only insofar as it is enacted, and its emerging figures have to do with empowerment strategies exercised in and from the cultural sphere. What the new social, ethnic, gender, gay and lesbian, religious or ecological movements demand is not only ideological representation but also socio-cultural recognition. They seek to become visible in their difference as citizens. This opens up a new mode for the political exercise of their rights, since this new visibility catalyzes the emergence of new political subjects. This was the subject visualized by feminism when it subverted the Left's profound machismo with its slogan: “the personal is political!” which came to embody both a sense of injury and victimization and a sense of recognition and empowerment.

This is the only way we will escape the illusory quest for the reincorporation of alterity into some unified whole, be it nation, political party, or religion. Citizenship rights, those rights exercised today by the different cultural communities that constitute a nation, will then take center stage. This is the new value that attributes the human universality of rights to the specificity of its very diverse modes of perception and expression.

\spaceHalf

\inright{\aKeyword[Participation]{theorizing+participation}}

\aQuoteB{de Souza}{2006}{338}\aQuoteInTextT{Together with the state,
despite the state, against the state: Social movements as ‘critical urban
planning’ agents}

\spaceHalf
\inright{participation in institutions}
Participation in institutionalized participatory channels can be useful under certain circumstances, but even if the partner is a ‘truly progressive and open government’ social movements have to be cautious and cultivate their capacity of (self-)criticism. Technical help from progressive intellectuals and professional planners can be very welcome and necessary, but social movements cannot abdicate control of the agenda of discussions to middle-class academics and NGOs—or the state apparatus.

\aQuoteB{Ackerly}{2000}{43}\aQuoteInTextT{Political Theory and Feminist Social Criticism}

According to Estlund, deliberative democracy requires only competent voters (1997: 185) and certain ``social and structural circumstances'' (1997: 190) which include allowing participation by all, a focus on common not individual or group interests, a ``shared conception of justice,'' fair evaluation of arguments, knowledge of one another's views, pluralism in life experience and culture, and the welfare of all participants suf®cient to enable people to participate in public deliberations (1997: 190±191).

\aQuoteB{Ackerly}{2000}{66, 67}\aQuoteInTextT{Political Theory and Feminist Social Criticism}

Like much of the tradition of feminism, its function is more broad than criticism about women's social standing. Third World feminist social criticism is social criticism. Moreover, though practically grounded and thus realizable, it is also theoretically useful. In fact, it offers a solution to the practical and theoretical problems deliberative democratic theorists had in describing principles and procedures for deliberation that were informed and inclusive, with broad participation without the tyranny of the majority,
the tyranny of the method, or the tyranny of the meeting.

Finally, in the real world, people don't want to and don't have time to participate in deliberations to the extent deliberative theorists would require.49 Thus, the theory that relies on participation (2) needs to explain either why people will participate willingly or why their lack of participation doesn't matter for the theory.

\aQuoteB{Ackerly}{2000}{115, 135}\aQuoteInTextT{Political Theory and Feminist Social Criticism}

Participation ± to participate freely, fully, and equally in the full range of community life, including its familial, social, economic and political decision making

For some people, effective participation in deliberation itself is ful®lling (regardless of particular successes or failures). But as discussed in chapter 2 for some people deliberative fora create obligations not opportunities. Children, family illness, and economic demands are possible competing obligations. Spending time in remote places and working uninterrupted are possible competing desires. If people are not participating because competing obligations are inhibiting their participation, critics need to consider the competing obligations as sources of inequality.

\spaceHalf

\inright{\aKeyword[Max Difference]{theorizing+right to the city+max difference}}
\aQuoteB{Dikeç}{2009}{8}\aQuoteInTextT{Space Politics and Justice}

Since the early 1980s, the shift of focus from ‘social development’ to ‘security’, from ‘prevention’ to ‘repression’, from ‘right to difference’ to ‘the republican model of integration’, and from ‘autogestion’ to ‘the republican pact’ did not ensue ‘naturally’ from the changing nature of problems, but followed, to an important extent, from different discursive articulations of the spaces urban policy.

\spaceHalf

\inright{\aKeyword[Max Difference]{theorizing+right to the city+max difference}}
\aQuoteW{Barbero}{2009}\aQuoteInTextT{Staging Citizenship: Performance, Politics, and Cultural Rights}

The visibility of the Other—and every difference is an opportunity for dominance in a class-based society—together with the diversity of each contested identity today (contested not only in relation to other identities but in relation to itself) is a constitutive part of the recognition of rights. This is expressed in the phonetic similarity and semantic articulation of visibilidad (visibility) and veedurías (community oversight committees): those practices of investigation and intervention by citizens in the public sphere. 

\aQuoteB{Ackerly}{2000}{192}\aQuoteInTextT{Political Theory and Feminist Social Criticism}

Mouffe's alternative model of citizenship recognizes citizenship as neither the source of one's identity nor an aspect of one's identity. Instead identities are determined through interaction with others and may vary according to context and those present (1992: 326). Thus, questions of identity are deliberatively determined, not given and static. Finally, Mouffe's view of citizenship has implications for community and the boundaries between public and private activity. In the context of interaction with others, citizens negotiate the appropriate boundaries of public and private, ``because every interaction is private while never immune from the public conditions prescribed by the principles of citizenship'' (1992: 325). 

\spaceHalf

\inright{\Autonomy and \SelfDetermination}

\aQuoteB{de Souza}{2006}{330}\aQuoteInTextT{Together with the state,
despite the state, against the state: Social movements as ‘critical urban
planning’ agents}

An autonomous society ‘institutes’ itself on the basis of freedom both from meta- physical constraints (e.g. religious or mythical foundations of laws and norms) and from political oppression

While adopting Castoriadis’ interpretation of the ‘autonomy project’ as a major source of politico-philosophical and ethical inspiration, I have also argued in several works that it is necessary to make this politico-social project more ‘operational’ for purposes of action hic et nunc—for instance, by means of finding a compromise between, on the one hand, a very ambitious level of thought and action (‘utopian’ dimension, ‘radical horizon’), and more or less modest tactical victories here and now (tactical, local gains in terms of reduction of heteronomy which can have important politico-pedagogical cumulative effects in the long run) on the other hand (Souza, 2000b, 2002). 

\aQuoteB{de Souza}{2010}{488}\aQuoteInTextT{Cities for people, not for profit}

\spaceHalf
\inright{ideological cop-optation}
As a very heterodox Marxist in many senses, Henri Lefebvre himself cultivated autogestion as a crucial political concept, while addressing at the same time pertinent criticisms towards the threat of an ideological co-optation of this notion;

%----------------------------------------

\startARemark{kommt noch zu Day and Nights}

\aQuoteB{de Souza}{2006}{333}\aQuoteInTextT{Together with the state,
despite the state, against the state: Social movements as ‘critical urban
planning’ agents}

\spaceHalf{drug trafficking}
\inright
Drug trafficking is an important challenge, not only for the state and for stateled urban planning (see Souza, 2005), but also for social movements and social activism in general (see Souza, 2000a, 2005). As far as the MTST is concerned, this challenge is not only related to its attempt to develop actions in favelas, but also due to the fact, that drug dealers or drug trafficking organizations can try to ‘territorialize’ ocupações: at the periphery of Guarulhos (metropolitan region of São Paulo) MTST militants were already threatened and expelled by drug traffickers in 2004 from one of the biggest settlements grounded by MTST, Anita Garibaldi.

\stopARemark

%---------------------------------------------------
% gets only displayed in unfinished mode

\showImperfection

%---------------------------------------------------

\stoptext

\stopcomponent
