\startcomponent component_Methodology_WhatShouldIDo
\product product_Thesis
\project project_MasterThesis

% definitions and macros
\environment envThesisAllEnvironments

% setup for table all cells
\setupTABLE[row][each]
[
	background=color,
	foreground=color,
	frame=on,
	rulethickness=2pt,
	corner=00,
	offset=2pt,
	backgroundcolor=black,
	foregroundcolor=white,
	framecolor=yellow,
]

\setupTABLE [y][first]
[	
	background=color,
	frame=off,
	rulethickness=2pt,
	foregroundcolor=black,
	backgroundcolor=yellow,
]

\define[]\sectionWhatShouldIDo{\section[methodology_whatshouldido]{What should I do?}}

\starttext

\startmode[tocLayout]

\sectionWhatShouldIDo

Defines concrete Methods and Tools used in this thesis.

\stopmode

\startmode[draft]

\sectionWhatShouldIDo

\inright{things done}
Where am I now? I know \gotoTextMark[who I am]{methodology_whoami} and \gotoTextMark[what I want to do]{methodology_whatdoiwant}. I determined a set of \gotoTextMark[demands]{methodology_whoami_motivation} and \gotoTextMark[attitudes]{methodology_whoami_nonauthoritarian} that constitute my personal and my research praxis. Hence I determined \abbrFull{AR} as the \gotoTextMark[framework for this research actions]{methodology_whoami_actionresearch}. Based on those concepts, I tried to demarcate the \gotoTextMark[scope of actions]{methodology_whatdoiwant} that could probably give this thesis a certain \gotoTextMark[relevance]{methodology_whoami_relevance}, relevant for me and for the struggle of the people.

I think its time now to become concrete and leave the space of imagination for a while.

\spaceHalf

\inright{unfold theory and praxis}
I would like to outline the realization of my \aKeyword[research actions]{research+actions} and \aKeyword[thesis theorizing]{thesis+theorizing} in the following sections. This outline is my attempt of a structure to allow \gotoTextMark[theorizing and actions]{methodology_whatshouldido_theoryvspraxis} to go hand in hand, to outline which \aKeyword[approaches]{thesis+methods} are used for \gotoTextMark[theorizing]{methodology_whatshouldido_methodtheorizing} and for \gotoTextMark[research actions]{methododology_whatshouldido_methodparticipantobservation} and which \aKeyword[tools]{thesis+tools} I considered as helpful to support \gotoTextMark[theorizing]{methodology_whatshouldido_toolstheorizing} and for the production of this \gotoTextMark[thesis and its content]{methodology_whatshouldido_toolscontent}.

\placetable[force]{What should I do? Unfold Theory and Praxis.}
{
\bTABLE
\bTR
	\bTH[nc=2, align={middle,lohi}] {\tt\bf theory and praxis unfold} \eTH
\eTR
\bTR
\bTD \color[yellow]{\tt methods}\blank[0.20cm] for theorizing and knowledge production\eTD
\bTD \color[yellow]{\tt methods}\blank[0.20cm] for realizing research actions\eTD
\eTR
\bTR
\bTD \color[yellow]{\tt tools}\blank[0.20cm] for theorizing and knowledge production\eTD
\bTD \color[yellow]{\tt tools}\blank[0.20cm] for thesis writing and content production \eTD
\eTR
\eTABLE
}

\showImperfection

\stopmode

\stoptext

\stopcomponent
