\startcomponent component_Theorizing_Reconstruction
\product product_Thesis
\project project_MasterThesis

% definitions and macros
\environment envThesisAllEnvironments
\environment envCfgThesisImages

\define[]\sectionTheorizingReconstruction{\section[theorizing_reconstruction]{Re//Construct//Themes}}

\starttext

\startmode[tocLayout]
\sectionTheorizingReconstruction

Reconstruct theorizing themes.

\stopmode

\startmode[draft]
\sectionTheorizingReconstruction

The pages are empty now and can now be rewritten. How to start \reconstructing what has been intended of becoming \deconstructed? I would like to start from the \poor as in the \gotoTextMark[previously determined sense]{text mark missing to the definition of the poor}, the \politicalSubject that is not recognized and that does not take part in the contemporary world. The \politicalSubject are those movements and individuals that struggle for emancipatory transformation.

\JRancier says that the \poor make the \refMissingSrc{invisible visible} in a world that is already configured and partitioned 

- How does the political subject look like?

- What does the political subject struggle for? for ruling and being ruled without having the qualification for ruling in contrast those that rule because they rule, ....

How does the political subject struggle? through politics meant as dissensus, through participation meant as the creation of new spaces first and for the complete dissolution into the political space finally

the political space is the space of the poor, where the worker is not attributed to a category

the political space is the space of autonomy and self determination

the political space is the space of max difference

\aQuoteInB{Kipfer}{2008}{204}
For Lefebvre, claims to “the right to the city” are the prism through which minimal difference may be transformed into maximal difference and fragments of abstract space may be connected in a quest to differential space. It helps to recall that Lefebvre treated the urban not only as a mediation of far and near order of totality. He also saw it as a (fleeting) form of centrality and difference, a point of convergence and “an ensemble of differences.”87 The right to difference is thus simply the flip- side of asserting the right to the city (centrality/power). Affirming the right to the city/difference does not mean celebrating actually existing manifestation of diversity per se, however. The liberal-pluralist diversity refers to reified forms of minimal difference (individualism, group pluralism).88 F

\aQuoteInB{Kipfer, Schmid, Goonewardena, Milgrom}{2008}{290}
Lefebvre offers a view of the urbanization process that is distinct from most others. He analyzes the urban not as accomplished reality but as possibility, a potential that is inherent in existing urbanization but can be realized only through fundamental social change: an urban revolution.The peculiar quality of this analysis is that it does not limit itself to a critique of the urbanization process but thinks through the implications of this process to lay bare its social possibilities.This reveals a potential that Lefebvre programmatically calls “urban society.”


\aQuoteInB{Kipfer, Schmid, Goonewardena, Milgrom}{2008}{293}
As Kipfer, Milgrom, and Andrew Shmuely remind us in this volume, there is also an important distinction between minimal and maximal difference. Minimal or induced difference tends toward formal identity that fragments everyday life and peripheralizes social groups. Maximal or produced difference implies a fundamental social transformation. Sources for maximal difference can be found both within the interstices of everyday life and in the midst of uprisings. For Lefebvre, difference is a multidimensional concept emerging from political struggles. It has to be

Lefebvre’s grand project envisions a possible path to this urban world in which unity is no longer opposed to difference, where the homogeneous no longer conflicts with the heterogeneous, and gatherings, encounters, and meetings—not without conflicts— will replace the struggle of individual urban elements that have become antinomies as a result of divisions: this urban space would provide the social basis for a radically transformed daily life that is open to possibility.

\aQuoteInB{Kipfer, Schmid, Goonewardena, Milgrom}{2008}{311}
Such alternative and oppositional claims for difference can take on very different forms and ways of expression: small-scale resistances, counter-projects, anti-imperial insurgencies, rebellions of the dispossessed in metropolitan centers such as the recent uprisings in Paris, as well as well-documented anti-globalization struggles and networked encounters. Struggles of peripheralized social groups against segregation and for empowerment can produce their own forms of centrality. Here, one can think of alternative social spaces created by sub- and counter-cultural groups or the oppositional centralities produced through mass mobilization (strikes, demonstrations, uprisings). The search for new centralities in a context of trans- national urbanization thus leads not only to global and capital cities (New York and London) but also to central places produced by counter-networks and mobilizations (Porto Alegre and Bamako).

\aQuoteInB{Kipfer, Goonewardena, Schmid, Milgrom}{2008}{8}
Lefebvre’s primarily political understanding of the urban revolution as a dialectical transformation of minimal into maximal difference (described in Le manifeste différentialiste, The Production of Space, and the third volume of The Critique of Everyday Life). This transformation can be achieved only by social struggles for political self-determination and a new spatial centrality, which help liberate difference from the alienating social constraints produced by capital, state, and patriarchy.



Autonomy 

As a germ, autonomy emerges when explicit and unlimited interrogation explodes on the scene – an interrogation that has bearing not on the “facts” but on the social imaginary significations and their possible grounding. 

This is a moment of creation, and it ushers in a new type of society and a new type of individuals. 

I am speaking intentionally of germ, for autonomy, social as well as individual, is a project. 

The rise of unlimited interrogation creates a new social-historical eidos: reflectiveness in the full sense, self-reflectiveness, as well as the individual and the institutions which embody it. 

The questions raised are, on the social level: Are our laws good? Are they just? Which laws ought we to make? And, on the individual level: Is what I think true? Can I know if it is true – and if so, how?... 

Autonomy comes from autos-nomos: [to give to] oneself one’s laws... Autonomy does not consist in acting according to a law discovered in an immutable reason and discovered once and for all. It is the unlimited self-questioning about the law and its foundations and the capacity, in light of this interrogation, to make, to do, and to institute [and therefore also, to say]. Autonomy is the reflective capacity of a reason creating itself in an endless movement, both as individual and social reason... 

If the autonomous society is that society which self-institutes itself explicitly and lucidly, the one that knows that it it-self posits its institutions and its significations, this means that it knows as well that they have no source other than its own instituting and signification-giving activity, no extrasocial guarantee. 

We thereby encounter once again the radical problem of democracy. Democracy, when it is true democracy, is the regime that explicitly renounces all ultimate guarantees and knows no limitations other than its self-limitation... This amounts to saying that democracy is the only tragic political regime – it is the only regime that takes risks, that faces openly the possibility of its self-destruction.

Cornelius Castoriadis, “Power, Politics, Autonomy” and “The Logic of Magmas and the Question of Autonomy,” both in The Castoriadis Reader [Oxford UP, 1991], pp. 163-63 and 316.




\startCitation
Political struggle is not a conflict between well defined interest groups; it is an opposition of logics that count the parties and parts of the community in different ways. 
\stopCitation






10 thesen: 10

What thus characterizes a democracy is pure chance or the
complete absence of qualifications for governing. Democracy is that state of exception
where no oppositions can function, where there is no pre-determined principle of role
allocation.

10 thesen: 12

 the 'power of the demos' means that those who rule are those who have no specificity in common, apart from their having no qualification for governing. Before being the name of a community, demos is the name of a part of the community: namely, the poor. The 'poor,' however, does not designate an economically disadvantaged part of the population; it simply designates the category of peoples who do not count, those who have no qualifications to part-take in arche, no qualification for being taken into account.

10 these: 13

The one who is 'unaccounted-for,'the one who has no speech to be heard, is the one of the demos.

10 thesen: 18

Politics cannot be deduced from the necessity of gathering people into communities. It is
an exception to the principles according to which this gathering operates. The 'normal' order of things is that human communities gather together under the rule of those qualified to rule -- whose qualifications are legitimated by the very fact that they are ruling. These governmental qualifications may be summed up according to two central principles: The first refers society to the order of filiation, both human and divine. This is the power of birth. The second refers society to the vital principle of its activities. This is the power of wealth. Thus, the 'normal' evolution of society comes to us in the progression from a government of birth to a government of wealth. Politics exists as a deviation from this normal order of things. It is this anomaly that is expressed in the nature of political subjects who are not social groups but rather forms of inscription of 'the (ac)count of the unaccounted-for.'

10 thesen: 19

There is politics as long as 'the people' is not identified with the race or a population,
inasmuch as the poor are not equated with a particular disadvantaged sector, and as long as the proletariat is not a group of industrial workers, etc... Rather, there is politics inasmuch as 'the people' refers to subjects inscribed as a supplement to the count of the parts of society, a specific figure of 'the part of those who have no-part.' 

And the politics of these categories has always consisted in re-qualifying these places, in getting them to be seen as the spaces of a community, of getting themselves to be seen or heard as speaking subjects (if only in the form of litigation); in short, participants in a common aisthesis. It has consisted in making what was unseen visible; in getting what was only audible as noise to be heard as speech; in demonstrating to be a feeling of shared 'good' or 'evil' what had appeared merely as an expression of pleasure or pain

10 thesen: 24

The essence of politics is dissensus. Dissensus is not the confrontation between interests
or opinions. It is the manifestation of a distance of the sensible from itself. Politics makes visible that which had no reason to be seen, it lodges one world into another (for instance, the world where the factory is a public space within the one where it is considered a private one, the world where workers speak out vis-à-vis the one where their voices are merely cries expressing pain). 

In contrast, the particular feature of political dissensus is that the partners are no more constituted than is the object or the very scene of discussion. The ones making visible the fact that they belong to a shared world the other does not see -- cannot take advantage of -- the logic implicit to a pragmatics of communication. The worker who argues for the public nature of a 'domestic' matter (such as a salary dispute) must indicate the world in which his argument counts as an argument and must demonstrate it as such for those who do not possess a frame of reference to conceive of it as argument. 

Political argument is at one and the same time the demonstration of a possible world where the argument could count as argument, addressed by a subject qualified to argue, upon an identified object, to an addressee who is required to see the object and to hear the argument that he or she 'normally' has no reason to either see or hear. It is the construction of a paradoxical world that relates two separate worlds. 

10 thesen: 25

Politics thus has no 'proper' place nor does it possess any 'natural' subjects. A
demonstration is political not because it takes place in a specific locale and bears upon a
particular object but rather because its form is that of a clash between two partitions of the sensible. 

A political subject is not a group of interests or ideas: It is the operator of a
particular mode of subjectification and litigation through which politics has its existence.
Political demonstrations are thus always of the moment and their subjects are always
provisional. Political difference is always on the shore of its own disappearance: the people are close to sinking into the sea of the population or of race, the proletariat borders on being confused with workers defending their interests, the space of a people's public demonstration is always at risk of being confused with the merchant's agora, etc.

10 these: 27

That the distinguishing feature of politics is the existence of a subject who 'rules' by the
very fact of having no qualifications to rule; that the principle of beginnings/ruling is
irremediably divided as a result of this, and that the political community is specifically a
litigious community

politics, along with philosophy's effort to resituate politics under the auspices of this law. The Gorgias, the Republic, the Politics, the Laws, all these texts reveal the same effort to efface the paradox or scandal of a 'seventh qualification'  make of democracy a simple case of the indeterminable principle of 'the government of the strongest,' against which one can only oppose a government of those who know [les savants]. These texts all reveal a similar strategy of placing the community under a unique law of partition and expelling the empty part of the demos from the communal body. 

10 these: 33

The thesis thus amounts to asserting that the logical telos of capitalism makes it so that politics becomes, once again, out dated. And then it concludes with either the mourning of politics before the triumph of an immaterial Leviathan, or its transformation into forms that are broken up, segmented, cybernetic, ludic, etc... -- adapted to those forms of the social that correspond to the highest stage of capitalism. It thus fails to recognize that in actual fact, politics has no reason for being in any state of the social and that the contradiction of the two logics is an unchanging given that defines the contingency and precariousness proper to politics. Via a Marxist detour, the 'end of politics' thesis -- along with the consensualist thesis -- grounds politics in a particular mode of life that identifies the political community with the social body, subsequently identifying political practice with state practice. The debate between the philosophers of the 'return of politics' and the sociologists of the 'end of politics' is thus a straightforward debate regarding the order in which it is appropriate to take the presuppositions of 'political philosophy' so as to interpret the consensualist practice of annihilating politics.

10 thesen: thesis 6

If politics is the outline of a vanishing difference, with the distribution of social parts
and shares, then it follows that its existence is in no way necessary, but that it occurs
as a provisional accident in the history of the forms of domination. It also follows
from this that political litigiousness has as its essential object the very existence of
politics.

10 thesen: these 8

The principal function of politics is the configuration of its proper space. It is to disclose the world of its subjects and its operations. The essence of politics is the manifestation of dissensus, as the presence of two worlds in one

\showImperfection

\stopmode

\stoptext

\stopcomponent
