% for \startRef \stopRef
\environment envCmdRTC
% for \nl macro
\environment envTextRTC

\startenvironment envLinksPernaforte

\define[]\myLinks%
{%
\startREF%
Prefeitura da Cidade de São Paulo, 2004. {\em Pesquisa de Legislação Municipal}, São Paulo: SAS. Available at: \goto{\hyphenatedurl{http://www3.prefeitura.sp.gov.br/cadlem/secretarias/negocios_juridicos/cadlem/integra.asp?alt=04082004P+000152004SAS}} [url(http://www3.prefeitura.sp.gov.br/cadlem/secretarias/negocios_juridicos/cadlem/integra.asp?alt=04082004P+000152004SAS)] [Accessed November 2, 2010].
\nl
Prefeitura da Cidade de São Paulo, 2010a. Portal da Prefeitura da Cidade de São Paulo. {\em Portal da Prefeitura da Cidade de São Paulo}. Available at: \goto{\hyphenatedurl{http://www.capital.sp.gov.br/portalpmsp/homec.jsp}} [url(http://www.capital.sp.gov.br/portalpmsp/homec.jsp)] [Accessed November 2, 2010].
\nl
Prefeitura da Cidade de São Paulo, 2010b. Secretaria Municipal de Segurança Urbana. {\em Portal da Prefeitura da Cidade de São Paulo}. Available at: \goto{\hyphenatedurl{http://www.prefeitura.sp.gov.br/cidade/secretarias/seguranca_urbana/guarda_civil/}} [url(http://www.prefeitura.sp.gov.br/cidade/secretarias/seguranca_urbana/guarda_civil/)] [Accessed November 2, 2010].
\nl
Rede Rua, 2010a. Associação Rede Rua. {\em Associação Rede Rua}. Available at: \goto{\hyphenatedurl{http://www.rederua.org.br/index.php?option=com_frontpage&Itemid=1}} [url(http://www.rederua.org.br/index.php?option=com_frontpage&Itemid=1)] [Accessed August 30, 2010].
\nl
Rede Rua, 2010b. Refeitório Comunitário do Povo da Rua. {\em Associação Rede Rua}. Available at: \goto{\hyphenatedurl{http://www.rederua.org.br/index.php?option=com_content&task=view&id=4&Itemid=7}} [url(http://www.rederua.org.br/index.php?option=com_content&task=view&id=4&Itemid=7)] [Accessed November 2, 2010].
\nl
\stopREF%
}

\define[]\myLocs%
{%
\startREF%
r3cl41m, 2010a. Centro Franciscano De Reinserção Social. Available at: \goto{\hyphenatedurl{http://www.openstreetmap.org/browse/node/913381513}} [url(http://www.openstreetmap.org/browse/node/913381513)] [Accessed November 2, 2010].
\nl
r3cl41m, 2010b. Praça da Sé. Available at: \goto{\hyphenatedurl{http://www.openstreetmap.org/browse/way/75488634}} [url(http://www.openstreetmap.org/browse/way/75488634)] [Accessed November 2, 2010].
\nl
r3cl41m, 2010c. Praça Ouvidor Pacheco E Silva. Available at: \goto{\hyphenatedurl{http://www.openstreetmap.org/browse/way/75488635}} [url(http://www.openstreetmap.org/browse/way/75488635)] [Accessed November 2, 2010].
\nl
r3cl41m, 2010d. Refeitório Comunitário de Povo da Rua. Available at: \goto{\hyphenatedurl{http://www.openstreetmap.org/browse/node/913381460}} [url(http://www.openstreetmap.org/browse/node/913381460)] [Accessed November 2, 2010].
\stopREF%
}

\define[]\myRefs%
{%
\startREF%
%separate links by newlines >> \nl
Horst, H., 2009. New Media Practices in Brazil, Part V: Mobile Phones. {\em Futures of Learning}. Available at: \goto{\hyphenatedurl{http://futuresoflearning.org/index.php/Firda_08/comments/new_media_practices_in_brazil_part_v_mobile_phones/}} [url(http://futuresoflearning.org/index.php/Firda_08/comments/new_media_practices_in_brazil_part_v_mobile_phones/)] [Accessed November 2, 2010].
\nl
\stopREF%
}

\stopenvironment